\paragraph{Description}
% \input{characteristics/description/Area Median Income}
Income as a percent of area median income of the household occupying the housing unit.

\paragraph{Distribution Data Sources}
% \input{characteristics/sources/Area Median Income}
\begin{itemize}
\item 
  Income from 2019 5-year PUMS from the University of Minnesota.
\item 
  Area Median Income definitions based on \href{https://www.huduser.gov/portal/datasets/il.html#data_2019}{2019 Income Limits from HUD}.
  
\end{itemize}

\paragraph{Direct Conditional Dependencies}
\input{characteristics/dependencies/Area Median Income}

\paragraph{Options}
The Area Median Income options are shown in Table \ref{table:hc_opt_area_median_income}. The Not Available option is for vacant units. The Area Median Income options do not set any modeling properties.

\input{characteristics/options/Area Median Income}

\paragraph{Distribution Assumptions}
% \input{characteristics/assumptions/Area Median Income}
\begin{enumerate}
\item
    Percent Area Median Income is calculated using annual household income in
  2019 USD (continuous, not binned) from 2019 5-year PUMS data and 2019
  income limits from HUD. These limits adjust for household size AND
  local housing costs (i.e., fair market rents). Income limits reported at
  county subdivisions are consolidated to County using a \href{https://mcdc.missouri.edu/applications/geocorr2014.html}{crosswalk}
  generated from Missouri Census Data Center's geocorr
  (2014), which has 2010 ACS housing unit count.
\item 
    For the 478 counties
    available in PUMS (60\%), the county-level income limits are used. For
    all others (40\%), PUMA-level income limits are used, which are
    converted from county-level using 2010 ACS housing unit count.
\end{enumerate}
