\paragraph{Description}
% \input{characteristics/description/ASHRAE IECC Climate Zone 2004 - Sub-CZ Split}
The climate zone, according to ASHRAE 169 in 2004 and IECC in 2012, where the sample is located. Climate zone where climate zone 2A is split between counties in (1) TX and LA, and (2) FL, GA, AL, and MS. Climate zone where climate zone 1A is split between counties in (1) HI, and (2) FL. See Figure \ref{fig:ashrae_169_2004_cz} for the climate zones and the climate zone 2A counties that are split between the states mentioned previously.

\paragraph{Distribution Data Sources}
% \input{characteristics/sources/ASHRAE IECC Climate Zone 2004 - Sub-CZ Split}
\begin{itemize}
    \item Spatial definitions are from the U.S.~Census Bureau as of July 1, 2015.
    \item Unit counts are from the American Community Survey 5-year 2016.
    \item Climate zone data are from ASHRAE 169 2004, IECC 2012, and \href{https://www.energy.gov/sites/prod/files/2015/10/f27/ba_climate_region_guide_7.3.pdf}{M.C. Baechler 2015}.
\end{itemize}

\paragraph{Direct Conditional Dependencies}
\input{characteristics/dependencies/ASHRAE IECC Climate Zone 2004 - Sub-CZ Split}

\paragraph{Options}
A set of counties defines each climate and moisture zone. Climate zones range from 1--8 and moisture zones are indicated by A, B, and C. Climate zone 2A is split between options ``2A---FL, GA, AL, MS'' and ``2A---TX, LA.''

\paragraph{Distribution Assumptions}
% \input{characteristics/assumptions/ASHRAE IECC Climate Zone 2004 - Sub-CZ Split}
\begin{itemize}
    \item This characteristic is used to better represent HVAC types in the 2A climate zone.
    \item This characteristic is used to better represent partial conditioning in the 1A climate zone.
\end{itemize}
