\paragraph{Description}
% \input{characteristics/description/Clothes Dryer}
The presence, rated efficiency, and fuel type of the clothes dryer in a housing unit.

\paragraph{Distribution Data Sources}
% \input{characteristics/sources/Clothes Dryer}
Constructed using U.S. EIA 2020 RECS microdata. 

\paragraph{Direct Conditional Dependencies}
\input{characteristics/dependencies/Clothes Dryer}

\paragraph{Options}
The ResStock options are shown in Table \ref{table:hc_opt_clothes_dryer}.

\input{characteristics/options/Clothes Dryer}

Property definitions are shown in Table \ref{table:hc_arg_def_clothes_dryer}. See the OpenStudio-HPXML \href{https://openstudio-hpxml.readthedocs.io/en/v1.10.0/workflow_inputs.html#hpxml-clothes-dryer}{Clothes Dryer} documentation for additional information.

\input{characteristics/properties/Clothes Dryer}

\paragraph{Distribution Assumptions}
% \input{characteristics/assumptions/Clothes Dryer}
Clothes dryer option is ``None'' if the clothes washer is not present.

Due to the low sample count, the input file is constructed by downscaling a housing unit sub-input file with a household sub-input file. The sub-input files have the following dependencies: 
housing unit sub-input file: dependencies = Geometry Building Type RECS, State, Heating Fuel, and Clothes Washer Presence, with the following fallback coarsening order:
\begin{enumerate}
    \item State coarsened to Census Division RECS without AK, HI 
    \item  Heating Fuel coarsened to Other Fuel, Wood and Propane combined 
    \item Heating Fuel coarsened to Fuel Oil, Other Fuel, Wood and Propane combined 
    \item Geometry Building Type RECS coarsened to SF/MF/MH
    \item  Geometry Building Type RECS coarsened to SF and MH/MF 
    \item  State coarsened to Census Division RECS 
    \item State coarsened to Census Region 
    \item State coarsened to National. 
\end{enumerate}

Household sub-input file: dependencies = Geometry Building Type RECS, Tenure, and Federal Poverty Level, with the following fallback coarsening order:
\begin{enumerate}
\item  State coarsened to Census Division RECS without AK, HI 
\item  Geometry Building Type RECS coarsened to SF/MF/MH 
\item  Geometry Building Type RECS coarsened to SF and MH/MF 
\item  Federal Poverty Level coarsened every 100\% 
\item Federal Poverty Level coarsened every 200\%
\item  State coarsened to Census Division RECS
\item State coarsened to Census Region
\item State coarsened to National.
\end{enumerate}

In combining the housing unit sub-input file and household sub-input file, the conditional relationships are ignored across Heating Fuel and Clothes Washer Presence, as well as across Tenure and Federal Poverty Level.
