\paragraph{Description}
% \input{characteristics/description/Cooling Setpoint Offset Period}
The time period(s) for the housing unit's heating setpoint offset.

\paragraph{Distribution Data Sources}
% \input{characteristics/sources/Cooling Setpoint Offset Period}
\begin{itemize}
    \item Constructed using U.S.~EIA 2020 RECS microdata.
\end{itemize}

\paragraph{Direct Conditional Dependencies}
\input{characteristics/dependencies/Cooling Setpoint Offset Period}

\paragraph{Options}
The options shown in Table \ref{table:hc_opt_cooling_setpoint_offset_period} combine day and night offset periods. The default for the day is from 9 AM to 5 PM and for the night is 10 PM to 7 AM. The options then shift these periods randomly up to 5 hours in either direction. The shifting of the periods is mainly to avoid the synchronization of HVAC systems all turning on and off simultaneously. The property values are hourly arrays for when the setup occurs (a value of 1), a setback (a value of -1), and when the setup or setback does not occur (a value of 0).

\input{characteristics/options/Cooling Setpoint Offset Period}

Property definitions are shown in Table \ref{table:hc_arg_def_cooling_setpoint_offset_period}.

\input{characteristics/properties/Cooling Setpoint Offset Period}

\paragraph{Distribution Assumptions}
% \input{characteristics/assumptions/Cooling Setpoint Offset Period}
\begin{itemize}
    \item For dependency conditions with low samples, the following dependency values are lumped in progressive order until there are enough samples: (1) lump buildings into Single-Family and Multifamily only, (2) lump buildings into Single-Family and Multifamily only, and lump nearby climate zones within A/B regions and separately 7AK and 8AK, and (3) lump all building types together and lump climate zones within A/B and separately 7AK and 8AK regions.
\end{itemize}
