\paragraph{Description}
\input{characteristics/description/Corridor}

\paragraph{Modeling Approach}
Single-family attached and multifamily buildings can have corridors, which are passageways between units. Interior corridors are enclosed and assumed to be conditioned, which are modeled by adiabatic walls being created for the wall of the unit that is adjacent to the corridor. Exterior corridors provide shading, but are not enclosed. The way this is modeled is to add a shading object to the front and/or the back of the unit. ResStock only allows multifamily units to have a double-loaded interior corridor. ResStock does not model energy use (e.g., lighting, plug load, or HVAC) associated with corridors; it only models their impact on the multifamily housing units.

\paragraph{Distribution Data Sources}
\input{characteristics/sources/Corridor}

\paragraph{Direct Conditional Dependencies}
\input{characteristics/dependencies/Corridor}

\paragraph{Options}
For Mobile Homes, Single-Family Detached, and Single-Family Attached building types the option assigned is ``Not Applicable.'' Multifamily units all have a ``Double-Loaded Interior'' corridor with a width of 10 feet. Options are shown in Table \ref{table:hc_opt_corridor}.

\input{tables/options/Corridor}

Property definitions are shown in Table~\ref{table:hc_arg_def_corridor}. See the OpenStudio-HPXML \href{https://openstudio-hpxml.readthedocs.io/en/v1.10.0/workflow_inputs.html#dwelling-units}{Dwelling Units} documentation for additional information.

\input{tables/properties/Corridor}

\paragraph{Distribution Assumptions}
\input{characteristics/assumptions/Corridor}
