\paragraph{Description}
% \input{characteristics/description/Dishwasher}
The presence and rated efficiency of the dishwasher.

\paragraph{Distribution Data Sources}
% \input{characteristics/sources/Dishwasher}
\begin{itemize}
\item Constructed using U.S. EIA 2020 RECS microdata. 
\end{itemize}

\paragraph{Direct Conditional Dependencies}
\input{characteristics/dependencies/Dishwasher}

\paragraph{Options}
The ResStock options are shown in Table \ref{table:hc_opt_dishwasher}. The ``None'' option is used for homes without a dishwasher.\footnote{ResStock currently does not account for hand washing of dishes in hot water in cases where no dishwasher is present.}

\input{characteristics/options/Dishwasher}

Property definitions are shown in Table \ref{table:hc_arg_def_dishwasher}. See the OpenStudio-HPXML \href{https://openstudio-hpxml.readthedocs.io/en/v1.10.0/workflow_inputs.html#hpxml-dishwasher}{Dishwasher} documentation for additional information.

\input{characteristics/properties/Dishwasher}

\paragraph{Distribution Assumptions}
% \input{characteristics/assumptions/Dishwasher}
The 2020 RECS survey does not contain ENERGY STAR rating of dishwashers. ENERGY STAR efficiency distributions with Geometry Building Type, Census Division RECS, Federal Poverty Level, and Tenure as dependencies are imported from RECS 2009.

Due to the low sample count, the input file is constructed with the following coarsening order:
\begin{enumerate}
    \item State coarsened to Census Division RECS with AK/HI separate 
    \item Geometry Building Type RECS coarsened to SF/MF/MH 
    \item  Geometry Building Type RECS coarsened to SF and MH/MF
    \item Federal Poverty Level coarsened every 100\% 
    \item Federal Poverty Level coarsened every 200\% 
    \item Vintage coarsened to every 20 years before 2000 and every 10 years subsequently
    \item  Vintage homes built before 1960 coarsened to pre-1960 
    \item  Vintage homes built after 2000 coarsened to 2000--20 
    \item  Census Division RECS with AK/HI separate coarsened to Census Division RECS 
    \item Census Division RECS to Census Region.
\end{enumerate}
