\paragraph{Description}
% \input{characteristics/description/Electric Vehicle Battery}
The type of electric vehicle and battery range in miles.

\paragraph{Distribution Data Sources}
% \input{characteristics/sources/Electric Vehicle Battery}
\begin{itemize}
  \item The 2023 Vehicle Stock Projection Data from NREL's TEMPO model
  \item EV Registration Data from Experian 2023
\end{itemize}

\paragraph{Direct Conditional Dependencies}
\input{characteristics/dependencies/Electric Vehicle Battery}

\paragraph{Options}
The options shown in Table \ref{table:hc_opt_electric_vehicle_battery} for the Electric Vehicle Battery characteristic determine the electric vehicle type and battery range in miles. These options do not specify if the unit has a vehicle, but rather the preference of the vehicle type and battery range if the household owned an electric vehicle. Every unit is assigned one of these options so that the vehicle type and battery range does not need to be sampled during an electric vehicle upgrade. The housing units at which an electric vehicle is modeled are specified by the Electric Vehicle Ownership characteristic.

\input{tables/options/Electric Vehicle Battery}

The Experian dataset is used to characterize the distribution of electric vehicles and associated battery sizes in the vehicle stock. We used the latest available data for the year 2023, which ensures that our analysis is based on the most current information regarding the electric vehicle battery stock. Although the vehicle data included information on internal combustion engine vehicles in addition to the battery electric vehicles, we filtered the dataset to focus exclusively on personal light-duty battery electric vehicles. In the dataset, there are four different categories of light-duty vehicles, including (a) Compact, (b) Midsize, (c) Sport Utility Vehicle (SUV), and (d) Pickup truck. Additionally, the dataset includes information on two total mileage ranges for the battery: (a) 200-mile range and (b) 300-mile range.

Then, for each electric vehicle type, we draw from Argonne National Laboratory's Autonomie20\footnote{Autonomie is the source of TEMPO's inputs about electric vehicle characteristics for both current day and future scenarios} vehicle powertrain simulation model for the electric vehicle energy consumption. The average driving speed is sourced from the 2017 NHTS which summarizes U.S. travel behavior (\cite{NHTS2017}). We assume that the average speed of electric vehicles is the same as the average speed of all vehicles.

Property definitions are shown in Table \ref{table:hc_arg_def_electric_vehicle_battery}. See the OpenStudio-HPXML \href{https://openstudio-hpxml.readthedocs.io/en/v1.10.0/workflow_inputs.html#hpxml-vehicles}{Vehicles} documentation for additional information.

\input{tables/properties/Electric Vehicle Battery}

\paragraph{Distribution Assumptions}
% \input{characteristics/assumptions/Electric Vehicle Battery}
\begin{itemize}
  \item Vehicle stock data starts with the Experian registration data and then is projected by TEMPO to 2023.
  \item If the household does not have an electric vehicle, the options represent the household preference.
\end{itemize}
