\paragraph{Description}
% \input{characteristics/description/Electric Vehicle Miles Traveled}
The number of miles an electric vehicle is driven in a year if the unit owns an electric vehicle.

\paragraph{Distribution Data Sources}
% \input{characteristics/sources/Electric Vehicle Miles Traveled}
The 2022 U.S. Federal Highway Administration National Household Travel Survey (NHTS) microdata.

\paragraph{Direct Conditional Dependencies}
\input{characteristics/dependencies/Electric Vehicle Miles Traveled}

\paragraph{Options}
The options shown in Table \ref{table:hc_opt_electric_vehicle_miles_traveled} for Electric Vehicle Miles Traveled characteristic specify miles traveled per year by the electric vehicle. These options do not specify if the unit has a vehicle, but rather the amount of miles the EV travels if the dwelling unit has an electric vehicle. Every unit is assigned one of these options so that the vehicle miles traveled does not need to be sampled during an electric vehicle upgrade. The units with an electric vehicle is specified by the Electric Vehicle Ownership characteristic. Because EVs drive less miles/year than ICE (\href{https://www.sciencedirect.com/science/article/pii/S254243512300404X?via%3Dihub#abs0015}{https://www.sciencedirect.com/science/article/pii/S254243512300404X?via\%3Dihub\#abs0015}), the max value is capped at 22,500 miles/yr and the distribution is shifted to reduce the mean.

\input{tables/options/Electric Vehicle Miles Traveled}

Property definitions are shown in Table \ref{table:hc_arg_def_electric_vehicle_miles_traveled}. See the OpenStudio-HPXML \href{https://openstudio-hpxml.readthedocs.io/en/v1.10.0/workflow_inputs.html#hpxml-vehicles}{Vehicles} documentation for additional information.

\input{tables/properties/Electric Vehicle Miles Traveled}

\paragraph{Distribution Assumptions}
% \input{characteristics/assumptions/Electric Vehicle Miles Traveled}
No assumptions are made.
