\paragraph{Description}
% \input{characteristics/description/Electric Vehicle Ownership}
The dwelling unit owns an electric vehicle.

\paragraph{Distribution Data Sources}
% \input{characteristics/sources/Electric Vehicle Ownership}
\begin{itemize}
  \item EV Registration Data from Experian 2023.
  \item 2019-5yrs Public Use Microdata Samples (PUMS). IPUMS USA, University of Minnesota, www.ipums.org.
  \item U.S. EIA 2020 Residential Energy Consumption Survey (RECS) microdata.

\end{itemize}

\paragraph{Direct Conditional Dependencies}
\input{characteristics/dependencies/Electric Vehicle Ownership}

\paragraph{Options}
The options ``No'' and ``Yes'' for Electric Vehicle Ownership characteristic determine if other EV properties are assigned.

\paragraph{Distribution Assumptions}
% \input{characteristics/assumptions/Electric Vehicle Ownership}
\begin{itemize}
  \item Due to low sample sizes, coarsening rules applied in the following order.
  \begin{enumerate}
    \item Federal Poverty Level lumped every 100\%
    \item Federal Poverty Level lumped every 200\%
    \item Building type is consolidated into three bins 1) single-family, 2) multi-family, and 3) mobile home
    \item Building type is consolidated into two bins 1) single-family and 2) multi-family and mobile home
  \end{enumerate}
  \item PUMA level battery EV saturation is calculated using a weighted average of the County level Experian data and ResStock unit counts for each County and PUMA.
  \item The RECS 2020 satuations for each segment in a given PUMA are scaled to match the Experian PUMA weighted averaged battery EV saturation using the segment unit counts from PUMS 2019-5yrs survey.
\end{itemize}
