\paragraph{Description}
% \input{characteristics/description/Geometry Foundation Type}
The type of foundation.

\paragraph{Distribution Data Sources}
% \input{characteristics/sources/Geometry Foundation Type}
\begin{itemize}
    \item The sample counts and sample weights are constructed using U.S.~EIA 2009 RECS microdata.
\end{itemize}

\paragraph{Direct Conditional Dependencies}
\input{characteristics/dependencies/Geometry Foundation Type}

\paragraph{Options}
The options of the Geometry Foundation type characteristic are shown in Table \ref{table:hc_opt_geometry_foundation_type}. Another name for Ambient foundations is pier and beam.

\input{characteristics/options/Geometry Foundation Type}

Property definitions are shown in Table \ref{table:hc_arg_def_geometry_foundation_type}.

\input{characteristics/properties/Geometry Foundation Type}

\paragraph{Distribution Assumptions}
% \input{characteristics/assumptions/Geometry Foundation Type}
\begin{itemize}
    \item All mobile homes have Ambient foundations.
    \item Multifamily buildings cannot have Ambient or Heated Basements foundations.
    \item Single-family attached buildings cannot have Ambient foundations.
    \item All foundation types are used across all housing types  except for mobile homes, which have constrained options.
    \item Because we need to assume a foundation type for ground-floor MF units, we use the lumped SFD+SFA distributions for MF2--4 and MF5+ building foundations. (RECS data for households in MF2--4 unit buildings are not useful since we do not know which floor the unit is on. RECS does not include foundation responses for households in MF5+ unit buildings.)
    \item For SFD and SFA, if no foundation type is specified, then the sample has Ambient foundation.
\end{itemize}
