\paragraph{Description}
% \input{characteristics/description/Geometry Garage}
The presence and size of an attached garage.

\paragraph{Distribution Data Sources}
% \input{characteristics/sources/Geometry Garage}
\begin{itemize}
    \item U.S.~EIA 2020 RECS microdata.
\end{itemize}

\paragraph{Direct Conditional Dependencies}
\input{characteristics/dependencies/Geometry Garage}

\paragraph{Options}
The options for the Geometry Garage characteristic are shown in Table \ref{table:hc_opt_geometry_garage}.

\input{characteristics/options/Geometry Garage}

Property definitions are shown in Table \ref{table:hc_arg_def_geometry_garage}.

\input{characteristics/properties/Geometry Garage}

\paragraph{Distribution Assumptions}
% \input{characteristics/assumptions/Geometry Garage}
Most of the assumptions below are not from the survey data, but are constraints of the geometry modeling in OpenStudio and are set to avoid errors.

\begin{itemize}
    \item Only Single-Family Detached homes are assigned a probability for attached garage.
    \item No garage for ambient (i.e., pier \& beam) foundation type.
    \item Due to modeling constraints restricting that garage cannot be larger or deeper than livable space: Single-family detached units that are 0--1499 square feet can only have a maximum of a 1-car garage.
    \item Single-family detached units that are 0--1499 square feet and 3+ stories cannot have a garage.
    \item The geometry stories distributions are all the same except for 0--1499 square feet and 3 stories.
    \item Single-family detached units that are 1500--2499 square feet cannot have a 3-car garage.
    \item Single-family detached units that are 2500--3999 square feet and a heated basement cannot have a 3-car garage.
    \item Due to low sample sizes, the following sets of dependencies are progressively lumped together.
    \begin{itemize}
    \item [1] Crawl, basements, and slab are lumped.
    \item [2] Story levels are lumped together.
    \item [3] Census Division RECS is grouped into Census Region.
    \item [4] Vintage ACS is grouped into: pre-1960, 1960-1999, and 2000+.
    \end{itemize}
\end{itemize}
