\paragraph{Description}
% \input{characteristics/description/Geometry Building Horizontal Location MF}
Location of the multifamily unit horizontally within the building (left, middle, right).

\paragraph{Distribution Data Sources}
% \input{characteristics/sources/Geometry Building Horizontal Location MF}
\begin{itemize}
    \item Calculated directly from the Geometry Number of Units MF and Geometry Stories characteristics.
\end{itemize}

\paragraph{Direct Conditional Dependencies}
\input{characteristics/dependencies/Geometry Building Horizontal Location MF}

\paragraph{Options}
The options of the Geometry Building Horizontal Location MF characteristic are shown in Table \ref{table:hc_opt_geometry_building_horizontal_location_mf}. The ``Not Applicable'' option is used for a pair of number of units and stories that cannot be sampled. For example, a 9-story, 2-unit multifamily building is unlikely to exist in reality and cannot be modeled in ResStock. ResStock does not model units in buildings with more stories than units. All building types other than multifamily receive the ``None'' option.

\input{tables/options/Geometry Building Horizontal Location MF}

Property definitions are shown in Table \ref{table:hc_arg_def_geometry_building_horizontal_location_mf}. See the OpenStudio-HPXML \href{https://openstudio-hpxml.readthedocs.io/en/v1.10.0/workflow_inputs.html#hpxml-building-construction}{Building Construction} documentation for additional information.

\input{tables/properties/Geometry Building Horizontal Location MF}

\paragraph{Distribution Assumptions}
% \input{characteristics/assumptions/Geometry Building Horizontal Location MF}
\begin{itemize}
    \item All probabilities are calculated assuming the building has double-loaded corridors (with some exceptions like 3 units in a single-story building).
\end{itemize}
