\paragraph{Description}
% \input{characteristics/description/Geometry Floor Area}
The conditioned floor area of the housing unit using bins from 2017--2019 American Housing Survey.

\paragraph{Distribution Data Sources}
% \input{characteristics/sources/Geometry Floor Area}
\begin{itemize}
    \item 2017 and 2019 American Housing Survey microdata.
\end{itemize}

\paragraph{Direct Conditional Dependencies}
\input{characteristics/dependencies/Geometry Floor Area}

\paragraph{Options}
The options of Geometry Floor Area characteristic are the American Housing Survey floor area bins and are shown in Table \ref{table:hc_opt_geometry_floor_area}. A representative conditioned floor area is assigned to each option in the ResStockArguments measure, using data from the 2017 and 2019 American Housing Surveys and disaggregated by housing type. The housing types are single-family detached, single-family attached, apartment, and manufactured homes. Currently, the same conditioned floor area values are used for single-family detached and manufactured homes.

\input{tables/options/Geometry Floor Area}

Property definitions are shown in Table \ref{table:hc_arg_def_geometry_floor_area}. See the OpenStudio-HPXML \href{https://openstudio-hpxml.readthedocs.io/en/v1.10.0/workflow_inputs.html#hpxml-building-construction}{Building Construction} documentation for additional information. The floor area is used many places in the OpenStudio-HPXML model workflow.

\input{tables/properties/Geometry Floor Area}

\paragraph{Distribution Assumptions}
% \input{characteristics/assumptions/Geometry Floor Area}
\begin{itemize}
\item
  Due to low sample count, the characteristic distributions are constructed by downscaling a core
  input file with 4 sub-input files of different dependencies.
\item Sub-input file 1 has dependencies: \textquotesingle Census
  Division\textquotesingle, \textquotesingle PUMA Metro
  Status\textquotesingle, \textquotesingle Geometry Building Type
  RECS\textquotesingle, \textquotesingle Income
  RECS2020\textquotesingle{}
\item
  Sub-input file 2 has dependencies: \textquotesingle Census Division\textquotesingle,
  \textquotesingle PUMA Metro Status\textquotesingle,
  \textquotesingle Geometry Building Type RECS\textquotesingle,
  \textquotesingle Tenure\textquotesingle{}
\item
  Sub-input file 3 has dependencies: \textquotesingle Census Division\textquotesingle,
  \textquotesingle PUMA Metro Status\textquotesingle,
  \textquotesingle Geometry Building Type RECS\textquotesingle,
  \textquotesingle Vintage ACS\textquotesingle{}
\item
  Sub-input file 4 has dependencies: \textquotesingle Census Division\textquotesingle,
  \textquotesingle PUMA Metro Status\textquotesingle,
  \textquotesingle Income RECS2020\textquotesingle,
  \textquotesingle Tenure\textquotesingle.
\item For each sub-input file, rows with
  \textless10 samples are replaced with coarsening dependency Census
  Region, followed by the national distribution.
\end{itemize}
