\paragraph{Description}
% \input{characteristics/description/Geometry Stories}
The number of stories in the building in which the housing unit is located.

\paragraph{Distribution Data Sources}
% \input{characteristics/sources/Geometry Stories}
\begin{itemize}
    \item U.S.~EIA 2009 RECS microdata.
\end{itemize}

\paragraph{Direct Conditional Dependencies}
\input{characteristics/dependencies/Geometry Stories}

\paragraph{Options}
The options for Geometry stories are shown in Table \ref{table:hc_opt_geometry_stories}. The stories of a building refer to the number of floors above grade. The number of stories does not include basements but would include finished attics.

\input{characteristics/options/Geometry Stories}

Property definitions are shown in Table \ref{table:hc_arg_def_geometry_stories}. See the OpenStudio-HPXML \href{https://openstudio-hpxml.readthedocs.io/en/v1.10.0/workflow_inputs.html#hpxml-building-construction}{Building Construction} documentation for additional information.

\input{characteristics/properties/Geometry Stories}

\paragraph{Distribution Assumptions}
% \input{characteristics/assumptions/Geometry Stories}
\begin{itemize}
    \item All mobile homes are 1 story.
    \item Single-Family Detached and Single-Family Attached use the STORIES field in RECS, whereas Multifamily with 5+ units uses the NUMFLRS field.
    \item Building types 2 Unit and 3 or 4 Unit use the stories distribution of Multifamily 5 to 9 Unit (capped at 4 stories) because RECS does not report stories or floors for multifamily with 2-4 units.
    \item The dependency on floor area bins is removed for multifamily with 5+ units.
    \item Vintage ACS rows for the 2010s are copied from the 2000-09 rows.
\end{itemize}
