\paragraph{Description}
% \input{characteristics/description/Ground Thermal Conductivity}
The thermal conductivity (in Btu/hr-ft-F) of the ground used in
foundation and geothermal heat pump heat transfer calculations.

\paragraph{Distribution Data Sources}
% \input{characteristics/sources/Ground Thermal Conductivity}
\begin{itemize}

\item
  Data from the Southern Methodist University Geothermal Laboratory. The data are from the Thermal Conductivity Observation in Content Model Format dataset. The data are available at \url{https://www.smu.edu/dedman/academics/departments/earth-sciences/research/geothermallab/datamaps/ngds-project}.
\end{itemize}

\paragraph{Direct Conditional Dependencies}
\input{characteristics/dependencies/Ground Thermal Conductivity}

\paragraph{Options}
ResStock options for Thermal Ground Conductivity, expressed in BTU/hr-ft-F, are shown in Table \ref{table:hc_opt_ground_thermal_conductivity}.

\input{characteristics/options/Ground Thermal Conductivity}

Property definitions are shown in Table \ref{table:hc_arg_def_ground_thermal_conductivity}. See the OpenStudio-HPXML \href{https://openstudio-hpxml.readthedocs.io/en/v1.10.0/workflow_inputs.html\#hpxml-site}{Site} documentation for additional information.

\input{characteristics/properties/Ground Thermal Conductivity}

\paragraph{Distribution Assumptions}
% \input{characteristics/assumptions/Ground Thermal Conductivity}
\begin{itemize}
\item
  The data obtained are from surveyed oil and gas well data.
\item
  The latitudes and longitudes were assigned to counties and the data were
  joined to the ResStock spatial lookup tables. In this process, 1,482 of
  59,332 samples did not have a FIPS match or did not have data and were
  dropped.
\item
  Due to limited data in climate zone 1A, data were pulled from samples
  in 1A plus Florida 2A.
\item
  Samples less than 0.5 Btu/hr-ft-F are assigned a value of 0.5
  Btu/hr-ft-F. Samples greater than 2.6 Btu/hr-ft-F are assigned a value
  of 2.6 Btu/hr-ft-F.
\end{itemize}
