\paragraph{Description}
% \input{characteristics/description/HVAC Secondary Heating Type}
The efficiency and type of the secondary heating system.

\paragraph{Distribution Data Sources}
% \input{characteristics/sources/HVAC Secondary Heating Type}
\begin{itemize}
\item Alaska-specific distribution is based on Alaska Retrofit Information System (2008 to 2022), maintained by the Alaska Housing Finance Corporation. Not implemented in baseline for other states.
\end{itemize}

\paragraph{Direct Conditional Dependencies}
\input{characteristics/dependencies/HVAC Secondary Heating Type}

\paragraph{Options}
The options for HVAC Secondary Heating Type are shown in Table \ref{table:hc_opt_hvac_secondary_heating_type}. Only homes in Alaska have secondary heating, so most housing units receive a ``None'' assignment. No modeling properties are assigned from this input file.

\input{tables/options/HVAC Secondary Heating Type}

\paragraph{Distribution Assumptions}
% \input{characteristics/assumptions/HVAC Secondary Heating Type}
\begin{itemize}
    \item For Alaska, we are using a field in ARIS that lumps multifamily 2--4 units and multifamily 5+ units buildings together. Data from the American Community Survey are used to distribute between these two building types.
    \item Ducted heating or heat pump cannot have ducted secondary heating.
    \item For Alaska, all heat pumps are assumed to be non-ducted mini-splits. 
    \item For Alaska, electricity cannot be a secondary heating fuel, therefore no secondary heating type. 
\end{itemize}
