\paragraph{Description}
% \input{characteristics/description/HVAC Secondary Heating Partial Space Conditioning}
The fraction of heating load served by secondary heating system. The remainder is served by the primary heating system.

\paragraph{Distribution Data Sources}
% \input{characteristics/sources/HVAC Secondary Heating Partial Space Conditioning}
\begin{itemize}
\item Alaska-specific distribution is based on Alaska Retrofit Information System (2008 to 2022), maintained by Alaska Housing Finance Corporation. Secondary heating partial space conditioning is not currently implemented in baseline for other states.
\end{itemize}

\paragraph{Direct Conditional Dependencies}
\input{characteristics/dependencies/HVAC Secondary Heating Partial Space Conditioning}

\paragraph{Options}
The options shown in Table \ref{table:hc_opt_hvac_secondary_heating_partial_space_conditioning} are the fraction of the load served for the secondary heating system.

\input{characteristics/options/HVAC Secondary Heating Partial Space Conditioning}

Property definitions are shown in Table \ref{table:hc_arg_def_hvac_secondary_heating_partial_space_conditioning}. See the OpenStudio-HPXML \href{https://openstudio-hpxml.readthedocs.io/en/v1.10.0/workflow_inputs.html#hpxml-heating-systems}{Heating Systems} documentation for additional information.

\input{characteristics/properties/HVAC Secondary Heating Partial Space Conditioning}

\paragraph{Distribution Assumptions}
% \input{characteristics/assumptions/HVAC Secondary Heating Partial Space Conditioning}
\begin{itemize}
    \item For Alaska, we are using a field in ARIS that lumps multifamily 2--4 units and multifamily 5+ units buildings together. Data from the American Community Survey are used to distribute between these two building types.
    \item For Alaska, the fraction of the load served by the secondary heating system is calculated as the ratio of annual energy used by secondary fuel and annual energy used by secondary and primary fuel.
\end{itemize}
