\paragraph{Description}
% \input{characteristics/description/HVAC Heating Efficiency}
The presence and efficiency of the primary heating system in the housing unit. This is the main input that determines the modeled heating system.

\paragraph{Distribution Data Sources}
% \input{characteristics/sources/HVAC Heating Efficiency}
\begin{itemize}
    \item The sample counts and sample weights are constructed using U.S.~EIA 2020 RECS microdata. 
    \item Shipment data based on ENERGY STAR ASHP shipments data and ENERGY STAR furnace shipments data. Efficiency data from Home Energy Saver are combined with age of equipment data from RECS. 
    \item Alaska-specific distribution is based on Alaska Retrofit Information System (2008 to 2022), maintained by Alaska Housing Finance Corporation.
\end{itemize}

\paragraph{Direct Conditional Dependencies}
\input{characteristics/dependencies/HVAC Heating Efficiency}

\paragraph{Options}
The options of the HVAC Heating Efficiency characteristic are shown in Table \ref{table:hc_opt_hvac_heating_efficiency} and assign the heating system type and efficiency. The system types are ducted ASHPs, electric baseboard, electric boiler, electric furnace, electric wall furnace, fuel boiler, fuel furnace, fuel wall/floor furnace, MSHPs, none, and shared heating. The Shared Heating option does not specify any properties. Shared Heating designates heating systems that serve multiple housing units in a multifamily building, and they have their own characteristics that set the properties; see Section \ref{sec:shared_systems}.

\input{tables/options/HVAC Heating Efficiency}

Property definitions are shown in Table (Table \ref{table:hc_arg_def_hvac_heating_efficiency}). See the OpenStudio-HPXML \href{https://openstudio-hpxml.readthedocs.io/en/v1.10.0/workflow_inputs.html#hpxml-heating-systems}{Heating System} documentation for additional information.

\input{tables/properties/HVAC Heating Efficiency}

\paragraph{Distribution Assumptions}
% \input{characteristics/assumptions/HVAC Heating Efficiency}
\begin{itemize}
    \item If a house has a wall furnace with fuel other than natural gas, the efficiency level based on natural gas from the Home Energy Saver weighted shipment efficiencies data is assigned.
    \item If a house has a heat pump with fuel other than electricity (presumed dual-fuel heat pump), the heating type is assumed to be furnace and not heat pump.
    \item The ENERGY STAR shipment volume for boiler was not available, so ENERGY STAR shipment volume for furnaces was used instead.
    \item Due to low sample size for some categories, the HVAC Has Shared System categories ‘Cooling Only’ and ‘None’ are combined for the purpose of querying Heating Efficiency distributions.
    \item For ‘other’ heating system types, we assign them to Electric Baseboard if fuel is Electric, and assign them to Wall/Floor Furnace if fuel is natural gas, fuel oil, or propane.
    \item For Other Fuel and Wood, the lowest efficiency systems are assumed.
    \item For Alaska, we are using a field in ARIS that lumps multifamily 2--4 units and multifamily 5+ units buildings together. Data from the American Community Survey are used to distribute between these two building types.
    \item For Alaska, electric space heaters are modeled as electric baseboards.
    \item For Alaska, Toyo/monitor direct-vent devices and other fuel space heaters are not modeled.
    \item For Alaska, fireplace and stoves are not modeled.
    \item For Alaska, all heat pumps (including geothermal) are assumed to be non-ducted ASHPs.
\end{itemize}
