\paragraph{Description}
% \input{characteristics/description/HVAC Cooling Partial Space Conditioning}
The fraction of cooling load served by the cooling system. This is approximately equal to the fraction of finished floor area served by the cooling system. Cooling load must be met at every time step for the portion of floor area covered, and does not represent intermittent cooling overtime. 

\paragraph{Distribution Data Sources}
% \input{characteristics/sources/HVAC Cooling Partial Space Conditioning}
\begin{itemize}
\item Constructed using U.S. EIA 2020 RECS microdata in Hawaii.
\item Constructed using U.S. EIA 2009 RECS microdata in all locations except Hawaii.
\end{itemize}

\paragraph{Direct Conditional Dependencies}
\input{characteristics/dependencies/HVAC Cooling Partial Space Conditioning}

\paragraph{Options}
Multiple levels of percent of floor area cooled are provided as shown in Table \ref{table:hc_opt_hvac_cooling_partial_space_conditioning}, plus an option for homes that have no cooling.

\input{characteristics/options/HVAC Cooling Partial Space Conditioning}

Property definitions are shown in Table \ref{table:hc_arg_def_hvac_cooling_partial_space_conditioning}. See the OpenStudio-HPXML \href{https://openstudio-hpxml.readthedocs.io/en/v1.10.0/workflow_inputs.html#hpxml-cooling-systems}{Cooling-Systems} documentation for additional information.

\input{characteristics/properties/HVAC Cooling Partial Space Conditioning}

\paragraph{Distribution Assumptions}
% \input{characteristics/assumptions/HVAC Cooling Partial Space Conditioning}
\begin{itemize}
    \item Central AC systems need to serve at least 60\% of the floor area.
    \item Heat pumps serve 100\% of the floor area in all locations except Hawaii because the system serves 100\% of the heated floor area. Partial cooling is common in cooling dominated climate.
    \item Due to low sample count, this input is constructed by downscaling a core sub-input file with 3 sub-input files of different dependencies. The sub-input files have the following dependencies: 
    \begin{itemize}
        \item input1 : ‘HVAC Cooling Type’, ‘ASHRAE IECC Climate Zone 2004---Sub-CZ Split’
        \item input2 : ‘HVAC Cooling Type’, ‘Geometry Floor Area Bin’
        \item input3 : ‘HVAC Cooling Type’, ‘Geometry Building Type RECS’
    \end{itemize}
\end{itemize}
