\paragraph{Description}
% \input{characteristics/description/HVAC Cooling Type}
The presence and type of primary cooling system in the housing unit.

\paragraph{Distribution Data Sources}
% \input{characteristics/sources/HVAC Cooling Type}
\begin{itemize}
\item U.S.~EIA 2020 RECS microdata. 
\item Alaska-specific distribution is based on Alaska Retrofit Information System (2008 to 2022), maintained by Alaska Housing Finance Corporation.
\end{itemize}

\paragraph{Direct Conditional Dependencies}
\input{characteristics/dependencies/HVAC Cooling Type}

\paragraph{Options}
The options for cooling system types are shown in Table \ref{table:hc_opt_hvac_cooling_type}. The options do not assign any modeling properties but are used as dependencies in other characteristics.

\input{characteristics/options/HVAC Cooling Type}

\paragraph{Distribution Assumptions}
% \input{characteristics/assumptions/HVAC Cooling Type}
\begin{itemize}
    \item Due to low sample sizes, fallback rules were applied, with coarsening of  (1) HVAC Heating type: Non-ducted heating and None, (2) Geometry building SF: Mobile, Single-family attached, Single-family detached, (3) Geometry building MF: Multifamily with 2--4 Units, Multifamily with 5+ Units, (4) Vintage Lump: 20-yr bins. 
    \item Homes having ducted heat pump for heating and electricity fuel are assumed to have ducted heat pump for cooling (separating from central AC category).
    \item Homes having non-ducted heat pump for heating are assumed to have non-ducted heat pump for cooling.
    \item For Hawaii, central air conditioning saturation is from RECS 2020 by heating type, ignoring all other dependencies
    \item For Hawaii, Non-Ducted Heat Pump saturation is underestimated because ResStock does not currently allow cooling-only Non-Ducted Heat Pumps. These samples are modeled as Room ACs
    \item For Alaska, we are using a field in ARIS that lumps multifamily 2--4 units and multifamily 5+ units buildings together. Data from the American Community Survey are used to distribute between these two building types.
    \item For Alaska, we are not modeling any central and room AC.
    \item For Alaska, cooling systems are never shared.
    \item Hawaii does not follow the same fallback rules. All distributions are custom adjusted so that state-level central air-conditioning saturation matches the state-level saturation in RECS2020.
\end{itemize}
