\paragraph{Description}
% \input{characteristics/description/HVAC Secondary Heating Fuel}
Secondary Heating Fuel for the housing unit. 

\paragraph{Distribution Data Sources}
% \input{characteristics/sources/HVAC Secondary Heating Fuel}
\begin{itemize}
\item Alaska-specific distribution is based on Alaska Retrofit Information System (2008 to 2022), maintained by Alaska Housing Finance Corporation. Secondary heating is not currently implemented in baseline for other states.
\end{itemize}

\paragraph{Direct Conditional Dependencies}
\input{characteristics/dependencies/HVAC Secondary Heating Fuel}

\paragraph{Options}
The options for the fuel type used by the secondary HVAC system are shown in Table \ref{table:hc_opt_hvac_secondary_heating_fuel}.

\input{characteristics/options/HVAC Secondary Heating Fuel}

Property definitions are shown in Table \ref{table:hc_arg_def_hvac_secondary_heating_fuel}. See the OpenStudio-HPXML \href{https://openstudio-hpxml.readthedocs.io/en/v1.10.0/workflow_inputs.html#hpxml-heating-systems}{heating systems} documentation for additional information.

\input{characteristics/properties/HVAC Secondary Heating Fuel}

\paragraph{Distribution Assumptions}
% \input{characteristics/assumptions/HVAC Secondary Heating Fuel}
\begin{itemize}
    \item For Alaska, we are using a field in ARIS that lumps multifamily 2--4 units and multifamily 5+ units buildings together. Data from the American Community Survey are used to distribute between these two building types.
    \item For Alaska, all wood is modeled as cord wood.
    \item For Alaska, when heating uses more than one fuel, the fuel with highest consumption is considered the primary (heating) fuel, and fuel with second highest usage (provided it is at least 10\% of total energy use across all fuels) is considered secondary (heating) fuel---except in case of electric heating, which is always assumed as primary (i.e., secondary heating fuel cannot be electricity). The rest of the fuels are ignored.
\end{itemize}
