\paragraph{Description}
% \input{characteristics/description/Income}
Income of the household occupying the housing unit.

\paragraph{Distribution Data Sources}
% \input{characteristics/sources/Income}
\begin{itemize}
\item
  2019 5-year PUMS from the University of Minnesota.
\end{itemize}

\paragraph{Direct Conditional Dependencies}
\input{characteristics/dependencies/Income}

\paragraph{Options}
The Income options are shown in Table \ref{table:hc_opt_income}. This characteristic has no modeling properties. Instead, it is used to construct other income characteristics and influences the distribution of housing characteristics as an indirect dependency.

\input{characteristics/options/Income}

\paragraph{Distribution Assumptions}
% \input{characteristics/assumptions/Income}
\begin{itemize}
\item
  In ACS, Income and Tenure are reported for occupied units only.
  Because we assume vacant units share the same Tenure distribution as
  occupied units, by extension, we assume this Income distribution
  applies to all units regardless of Vacancy Status. For reference,
  57445 / 140160 rows have sampling\_probability \textgreater= 1/550,000.\footnote{550,000 is the typical sample size for ResStock, indicating that these rows are likely to get sampled.}
  Of those rows, 2961 (5\%) were replaced due to low samples in the
  following process: Where sample counts are less than 10 (79145 /
  140160 relevant rows), the Census Division by PUMA Metro Status
  average distribution has been inserted first (76864), followed by
  Census Division by
  `Metro'/`Non-metro'
  average distribution (1187), followed by Census Region by PUMA Metro
  Status average distribution (282), followed by Census Region by
  `Metro'/`Non-metro'
  average distribution (112).
\end{itemize}
