\paragraph{Description}
% \input{characteristics/description/Infiltration}
Total infiltration to the dwelling unit.

\paragraph{Distribution Data Sources}
% \input{characteristics/sources/Infiltration}
\begin{itemize}

\item
  Distributions are based on the cumulative distribution functions from
  the \href{http://resdb.lbl.gov/}{Residential Diagnostics Database (ResDB)}.
\item
  Alaska-specific distribution is based on Alaska Retrofit Information
  System (2008 to 2022), maintained by Alaska Housing Finance
  Corporation.
\end{itemize}

\paragraph{Direct Conditional Dependencies}
\input{characteristics/dependencies/Infiltration}

\paragraph{Options}
All infiltration options in ResStock are provided in air changes per hour (ACH) at 50 Pascals, as calculated by a blower door test, and are shown in Table \ref{table:hc_opt_infiltration}.

\input{tables/options/Infiltration}

Property definitions are shown in Table \ref{table:hc_arg_def_infiltration}. See the OpenStudio-HPXML \href{https://openstudio-hpxml.readthedocs.io/en/v1.10.0/workflow_inputs.html##hpxml-air-infiltration}{Air Infiltration} documentation for additional information.

\input{tables/properties/Infiltration}

\paragraph{Distribution Assumptions}
% \input{characteristics/assumptions/Infiltration}
\begin{itemize}

\item
  All ACH50 are based on Single-Family Detached blower door tests.
\item
  Climate zones that are copied: 2A to 1A, 6A to 7A, and 6B to 7B.
\item
  Vintage bins that are copied: 2000s to 2010s, 1950s to 1940s, 1950s to
  \textless1940s.
\item
  Homes are assumed to not be Weatherization Assistance Program
  qualified and not ENERGY STAR certified.
\item
  Climate zones 7AK and 8AK are averages of 6A and 6B.
\item ResStock models multi-family and SFA units with the unit total air leakage type. The unit total air leakage assume that some of the sampled ACH50 value goes to neighboring units. The model infiltration value to the exterior is a smaller infiltration value that what is sampled and is adjusted by the ratio of exterior envelope surface area to total envelope surface area. The modeled infiltration to the exterior is reported in the results.
\item
  For Alaska, we are using a field in ARIS that lumps multifamily 2--4
  units and multifamily 5+ units buildings together. Data from the
  American Community Survey are used to distribute proportionally between these two
  building types.
\item
  For Alaska, Infiltration ACH50 values are calculated based on CFM50
  from blower door test and estimated volume of the home.
\end{itemize}
