\paragraph{Description}
% \input{characteristics/description/Metropolitan and Micropolitan Statistical Area}
The U.S.~Metropolitan Statistical Area (MSA) or Micropolitan Statistical Area (MicroSA) where sample is located. The U.S.~Census defines a set of counties as Core-Based Statistical Areas (CBSAs). These CBSAs are either assigned a MicroSA or combined into a larger MSA. According to the U.S.~Census, each metropolitan statistical area must have at least one urban area of 50,000 or more inhabitants. According to the U.S.~Census, each MicroSA must have at least one urban area of at least 10,000 but less than 50,000 population.

\paragraph{Distribution Data Sources}
% \input{characteristics/sources/Metropolitan and Micropolitan Statistical Area}
\begin{itemize}

\item
  Spatial definitions are from the U.S.~Census Bureau as of July 1,
  2015.
\item
  Unit counts are from the American Community Survey 5-year 2016.
\item
  County-MSA crosswalk comes from the Quarterly Census of Employment and
  Wages NAICS-based data between 2013 and 2022 by the U.S.~Bureau of Labor
  Statistics
  (\url{https://www.bls.gov/cew/classifications/areas/county-msa-csa-crosswalk.htm}).
\end{itemize}

\paragraph{Direct Conditional Dependencies}
\input{characteristics/dependencies/Metropolitan and Micropolitan Statistical Area}

\paragraph{Options}
Options of the Metropolitan and Micropolitan Statistical Area characteristic are structured by having the name of the MSA or MicroSA, a comma, the State abbreviation, and either ``MSA'' or ``MicroSA.'' An example is ``Albany-Schenectady-Troy, NY MSA,'' which corresponds to the Albany-Schenectady-Troy MSA in New York State.

\paragraph{Distribution Assumptions}
% \input{characteristics/assumptions/Metropolitan and Micropolitan Statistical Area}
No assumptions are made.

