\paragraph{Description}
% \input{characteristics/description/Misc Extra Refrigerator}
The presence and rated efficiency of the secondary refrigerator.

\paragraph{Distribution Data Sources}
% \input{characteristics/sources/Misc Extra Refrigerator}
\begin{itemize}
\item 

Constructed using U.S. EIA 2020 RECS microdata. 
\item Age of refrigerator converted to efficiency levels using ENERGY STAR shipment-weighted efficiencies by year data from Home Energy Saver.\footnote{For more information, see http://hes-documentation.lbl.gov/.} %Check the comments in: HES-Refrigerator\_Age\_vs\_Efficiency.tsv 
\end{itemize}

\paragraph{Direct Conditional Dependencies}
\input{characteristics/dependencies/Misc Extra Refrigerator}

\paragraph{Options}
Extra refrigerator options shown in Table \ref{table:hc_opt_misc_extra_refrigerator} are specified using the same Energy Factor (EF) and annual rated kWh options as primary refrigerators.

\input{characteristics/options/Misc Extra Refrigerator}

Property definitions are shown in Table \ref{table:hc_arg_def_misc_extra_refrigerator}. See the OpenStudio-HPXML \href{https://openstudio-hpxml.readthedocs.io/en/v1.10.0/workflow_inputs.html#hpxml-refrigerators}{Refrigerators} documentation for additional information.

\input{characteristics/properties/Misc Extra Refrigerator}

The usage multiplier varies by state and is set to account for the presence of tertiary refrigerators and beyond, see Table \ref{table:hc_opt_state}.

\input{characteristics/options/State}

\paragraph{Distribution Assumptions}
% \input{characteristics/assumptions/Misc Extra Refrigerator}
The current year is assumed to be 2022. 
Currently, each year has its own distribution and then we average out the distributions to get the distribution for the age bins. EF for all years are weighted equally when calculating the average distribution for the age bins. ENERGY STAR distributions from 2009 dependent on Geometry Building Type RECS, Federal Poverty Level, and Tenure are used to calculate efficiency distribution in RECS 2020. ENERGY STAR refrigerators assumed to be 10\% more efficient than standard. Due to the low sample count, the input file is constructed by downscaling a housing unit sub-input file with a household sub-input file. The sub-input files have the following dependencies: housing unit sub-input file: dependencies = Geometry Building Type RECS, State, and Vintage, with the following fallback coarsening order: 
\begin{enumerate}
    \item  State coarsened to Census Division RECS with AK/HI separate 
    \item Geometry Building Type RECS coarsened to SF/MF/MH 
\item Geometry Building Type RECS coarsened to SF and MH/MF 
\item Vintage with Vintage ACS 
\item Vintage with combined 1960s 
\item Vintage with combined 1960s and post 2000s 
\item Census Division RECS with AK/HI separate coarsened to Census Division RECS
\item Census Division RECS to Census Region.
\end{enumerate}
Census Region to National Assumption: Household sub-input file : dependencies = Geometry Building Type RECS, State, Tenure, and Federal Poverty Level, with the following fallback coarsening order:
\begin{enumerate}
\item State coarsened to Census Division RECS with AK/HI separate
\item Geometry Building Type RECS coarsened to SF/MF/MH 
\item  Geometry Building Type RECS coarsened to SF and MH/MF 
\item  Federal Poverty Level coarsened every 100\% 
\item  Federal Poverty Level coarsened every 200\% 
\item Census Division RECS with AK/HI separate coarsened to Census Division RECS 
\item Census Division RECS to Census Region 
\item Census Region to National. 

\end{enumerate}
In combining the housing unit sub-input file and household sub-input file, the conditional relationships are ignored across (Heating Fuel, [Tenure, Federal Poverty Level]).
