\paragraph{Description}
% \input{characteristics/description/Misc Hot Tub Spa}
The presence and heating fuel of a hot tub/spa at the housing unit.

\paragraph{Distribution Data Sources}
% \input{characteristics/sources/Misc Hot Tub Spa}
Constructed using U.S. EIA 2020 RECS microdata. 

\paragraph{Direct Conditional Dependencies}
\input{characteristics/dependencies/Misc Hot Tub Spa}

\paragraph{Options}
Options for the Misc Hot tub Spa characteristic are shown in Table \ref{table:hc_opt_misc_hot_tub_spa}. The None option is used when the housing unit does not have a hot tub. The “Other Fuel” option is currently not modeled in ResStock and will result in no energy consumption.

\input{characteristics/options/Misc Hot Tub Spa}

Property definitions are shown in Table \ref{table:hc_arg_def_misc_hot_tub_spa}. See the OpenStudio-HPXML \href{https://openstudio-hpxml.readthedocs.io/en/v1.10.0/workflow_inputs.html#hpxml-permanent-spas}{Permanent Spas} documentation for additional information.

\input{characteristics/properties/Misc Hot Tub Spa}

\paragraph{Distribution Assumptions}
% \input{characteristics/assumptions/Misc Hot Tub Spa}
Due to the low sample count, the input file is constructed by downscaling a housing unit sub-input file with a household sub-input file. The sub-input files have the following dependencies: 

housing unit sub-input file  dependencies = Geometry Building Type RECS, State, and Heating Fuel, with the following fallback coarsening order:
\begin{enumerate}
    \item State coarsened to Census Division RECS with AK/HI separate 
    \item  Heating Fuel coarsened to Other Fuel, Wood and Propane combined
    \item Heating Fuel coarsened to Fuel Oil, Other Fuel, Wood and Propane combined
    \item Geometry Building Type RECS coarsened to SF/MF/MH
    \item  Geometry Building Type RECS coarsened to SF and MH/MF 
    \item  Census Division RECS with AK/HI separate coarsened to Census Division RECS 
    \item Census Division RECS to Census Region 
    \item Census Region to National.  
\end{enumerate}
Household sub-input file: dependencies = Geometry Building Type RECS, State, Tenure, and Federal Poverty Level, with the following fallback coarsening order:
\begin{enumerate}
    \item State coarsened to Census Division RECS with AK/HI separate 
    \item  Geometry Building Type RECS coarsened to SF/MF/MH 
    \item  Geometry Building Type RECS coarsened to SF and MH/MF 
    \item  Federal Poverty Level coarsened every 100\% 
    \item Federal Poverty Level coarsened every 200\% 
    \item Census Division RECS with AK/HI separate coarsened to Census Division RECS 
    \item Census Division RECS to Census Region 
    \item Census Region to National. 
\end{enumerate}
In combining the housing unit sub-input file and household sub-input file, the conditional relationships are ignored across Heating Fuel, as well as across Tenure and Federal Poverty Level.
