\paragraph{Description}
% \input{characteristics/description/Refrigerator}
The presence and rated efficiency of the primary refrigerator.

\paragraph{Distribution Data Sources}
% \input{characteristics/sources/Refrigerator}
Constructed using U.S. EIA 2020 RECS microdata. Age of refrigerator converted to efficiency levels using ENERGY STAR shipment-weighted efficiencies by year data from Home Energy Saver.\footnote{For more information, see http://hes-documentation.lbl.gov/.} 

\paragraph{Direct Conditional Dependencies}
\input{characteristics/dependencies/Refrigerator}

\paragraph{Options}
ResStock options shown in Table \ref{table:hc_opt_refrigerator} differentiate primary refrigerators based on their efficiency level. A ``None'' option is used for housing units that do not have a refrigerator.

\input{characteristics/options/Refrigerator}

Property definitions are shown in Table \ref{table:hc_arg_def_refrigerator}. See the OpenStudio-HPXML \href{https://openstudio-hpxml.readthedocs.io/en/v1.10.0/workflow_inputs.html#hpxml-refrigerators}{Refrigerators} documentation for additional information.

\input{characteristics/properties/Refrigerator}

\paragraph{Distribution Assumptions}
% \input{characteristics/assumptions/Refrigerator}
The current year is assumed to be 2022. Currently, each year has its own distribution and then we average out the distributions to get the distribution for the age bins. The Energy Factor for all years are weighted equally when calculating the average distribution for the age bins. ENERGY STAR distributions from 2009 dependent on Geometry Building Type RECS, Federal Poverty Level, and Tenure are used to calculate efficiency distribution in RECS2020. ENERGY STAR Refrigerators are assumed to be 10\% more efficient than standard. Due to the low sample count, the following coarsening rules are incorporated.
\begin{enumerate}
    \item  State coarsened to Census Division RECS, with AK/HI separate.
    \item Geometry Building Type RECS coarsened to SF/MF/MH 
    \item Geometry Building Type RECS coarsened to SF and MH/MF 
    \item  Vintage with Vintage ACS 
    \item Vintage with combined 1960s 
    \item Vintage with combined 1960s and post 2000s 
    \item  Federal Poverty Level coarsened every 100\% 
    \item  Federal Poverty Level coarsened every 200\% 
    \item Census Division RECS with AK/HI separate coarsened to Census Division RECS 
    \item  Census Division RECS to Census Region 
    \item Census Region to National. 
\end{enumerate}
