\paragraph{Description}
% \input{characteristics/description/State Metro Median Income}
State Metro Median Income of the household occupying the housing unit.
This is different from State Median Income in that the Income Limits are
differentiated by metro and nonmetro regions of the state.

\paragraph{Distribution Data Sources}
% \input{characteristics/sources/State Metro Median Income}
\begin{itemize}
\item
  Income from 2019 5-year PUMS from the University of Minnesota.
\item
  Income Limits derived from 2019 5-year PUMS from the University of Minnesota and 2019 median income by state and metro/nonmetro area from HUD.
\end{itemize}

\paragraph{Direct Conditional Dependencies}
\input{characteristics/dependencies/State Metro Median Income}

\paragraph{Options}
The State Metro Median Income options are shown in Table \ref{table:hc_opt_state_metro_median_income}. The Not Available option is for vacant units. The State Metro Median Income options do not set any modeling properties.

\input{tables/options/State Metro Median Income}

\paragraph{Distribution Assumptions}
% \input{characteristics/assumptions/State Metro Median Income}
\begin{itemize}
\item
  Percent State Metro Median Income is calculated using annual household
  income in 2019 USD (continuous, not binned) from 2019 5-year PUMS data
  and 2019 median income by state and metro/nonmetro area from HUD. A
  County Metro Status-differentiated Income Limits table is derived from
  the median income table by adjusting for household size, which is consistent with the method of generating state income limits by HUD.
\end{itemize}
