\paragraph{Description}
% \input{characteristics/description/Water Heater Location}
Location of the water heater.

\paragraph{Distribution Data Sources}
% \input{characteristics/sources/Water Heater Location}
\begin{itemize}
\item
  U.S. EIA 2020 RECS microdata.
\end{itemize}

\paragraph{Direct Conditional Dependencies}
\input{characteristics/dependencies/Water Heater Location}

\paragraph{Options}
The options shown in Table \ref{table:hc_opt_water_heater_location} are spaces where the water heater can be located. The Conditioned Mechanical Room option is only used for multifamily units with shared water heating.

\input{tables/options/Water Heater Location}

Property definitions are shown in Table \ref{table:hc_arg_def_water_heater_location}. See the OpenStudio-HPXML \href{https://openstudio-hpxml.readthedocs.io/en/v1.10.0/workflow_inputs.html#hpxml-water-heating-systems}{Water Heating Systems} documentation for additional information.

\input{tables/properties/Water Heater Location}

\paragraph{Distribution Assumptions}
% \input{characteristics/assumptions/Water Heater Location}
\begin{itemize}
\item
  H2OMAIN = other is equally distributed among attic and crawlspace.
\item
  H2OMAIN does not apply to multifamily, therefore Water heater
  location for multifamily with in-unit water heater is taken after the
  combined distribution of other building types.
\item
  Out-of-unit water heater is assumed to be in Conditioned Mechanical
  Room. Per expert judgment, water heaters cannot be outside or in
  vented spaces for IECC Climate Zones 4-8 due to pipe-freezing risk.
\item
  Where samples \textless{} 10, data are aggregated in the following
  order:
  \begin{itemize}
\item
  Building Type lumped into single-family, multifamily, and mobile
  home.
\item
  1 + Foundation Type combined. 
\item 
2 + Attic Type combined
\item
  3 + Garage combined.
\item
  Single/Multifamily + Foundation combined + Attic combined +
  Garage combined.
\item
  5 + pre-1960 combined.
\item
  5 + pre-1960 combined/post-2020 combined.
\item
  7 + IECC Climate Zone lumped into: 1-2+3A, 3B-3C, 4, 5, 6, 7 except
  AK, 7AK-8AK.
\item
  7 + IECC Climate Zone lumped into: 1-2-3, 4-8.
\end{itemize}
\end{itemize}
