\paragraph{Description}
% \input{characteristics/description/Water Heater Efficiency}
The efficiency and type of the water heater by heating fuel.

\paragraph{Distribution Data Sources}
% \input{characteristics/sources/Water Heater Efficiency}
\begin{itemize}
\item
  U.S. EIA 2020 RECS microdata.
\item
  Heat pump water heaters: 2016-17 RBSA II for WA and OR; Butzbaugh
  et al. (\href{https://www.osti.gov/biblio/1433775}{2017}). \textit{US HPWH Market Transformation: Where
  We've Been and Where to Go Next} for remainder of
  regions.
\item
  Penetration of HPWH for Maine (6.71\%) calculated based on total
  number of HPWH units (from AWHI Stakeholder Meeting 12/08/2022) and total
  housing units (from \url{https://www.census.gov/quickfacts/ME}).
\end{itemize}

\paragraph{Direct Conditional Dependencies}
\input{characteristics/dependencies/Water Heater Efficiency}

\paragraph{Options}
Water Heater Efficiency options shown in Table \ref{table:hc_opt_water_heater_efficiency} define the technical details of the standalone water heaters and solar thermal water heaters with storage backup. The options for solar water heaters in ResStock distinguishes by orientation and backup fuel. The tilt of the collector is set to roof pitch for all options. The azimuth of the collector varies by option, with East (90\degree), South (180\degree), West (270\degree), and North (0\degree) orientations available.
All solar water heaters are modeled as two-tank systems, where the backup has its own storage separately from the primary tank. While this may be the common configuration for fuel backup systems, it is less common for electric backup systems, which often use a single tank with integrated solar and electric heating elements. To model a typical solar water heater with a single tank that has backup heating elements, the secondary tank is given a R-6.2 jacket to reduce the standby loss of the secondary tank. R-6.2 is the highest R-value allowable without causing OS-HPXML validation error.

\input{characteristics/options/Water Heater Efficiency}

Property definitions are shown in Table \ref{table:hc_arg_def_water_heater_efficiency}. See the OpenStudio-HPXML \href{https://openstudio-hpxml.readthedocs.io/en/v1.10.0/workflow_inputs.html#hpxml-water-heating-systems}{Water Heating Systems} and \href{https://openstudio-hpxml.readthedocs.io/en/v1.10.0/workflow_inputs.html#hpxml-solar-thermal}{Solar Thermal} documentation for additional information.

\input{characteristics/properties/Water Heater Efficiency}

\paragraph{Distribution Assumptions}
% \input{characteristics/assumptions/Water Heater Efficiency}
\begin{itemize}
\item
  Water heater blanket is used as a proxy for premium storage tank water
  heaters.
\item
  Heat Pump Water Heaters are added in manually as they are not in the
  survey; all have default efficiency: Electric Heat Pump, 50 gal, 3.45 UEF.
\item
  Solar thermal water heaters: backup is informed by secondary water heater fuel type; electric backup is assumed if no secondary water heating. All collectors are assumed 40 sqft, roof pitch; collector orientation diversity is based on rooftop solar PV orientation for those with electric backup; for fuel backup, it is assumed south-facing.
\item
  Due to low sample sizes, fallback rules are applied, with lumping of:
  
  \begin{itemize}
  \item
    State: Census Division RECS
  \item
    State: Census Region
    \item
    State: National
  \end{itemize}
\end{itemize}
