\paragraph{Description}
% \input{characteristics/description/Windows}
Construction type and efficiency levels of windows.

\paragraph{Distribution Data Sources}
% \input{characteristics/sources/Windows}
\begin{itemize}

\item
  U.S.~EIA 2020 RECS microdata.
\end{itemize}

\paragraph{Direct Conditional Dependencies}
\input{characteristics/dependencies/Windows}

\paragraph{Options}
ResStock options vary across number of panes, low-emissivity coating, and frame material as shown in Table \ref{table:hc_opt_windows}.

\input{characteristics/options/Windows}

Property definitions are shown in Table \ref{table:hc_arg_def_windows}. See the OpenStudio-HPXML \href{https://openstudio-hpxml.readthedocs.io/en/v1.10.0/workflow_inputs.html#hpxml-windows}{Windows} documentation for additional information.

\input{characteristics/properties/Windows}

\paragraph{Distribution Assumptions}
% \input{characteristics/assumptions/Windows}
\begin{itemize}

\item
  All Triple-Pane options assumed to be low-e.
\item
  Only breaking out clear and low-e windows for the Double, Non-Metal
  frame type.
\item
  Source of low-e distribution is based on engineering judgment,
  informed by high-level sales trends observed in Ducker Worldwide
  studies of the U.S.~market for windows, doors and skylights.
\item
  Due to low sample sizes, the following adjustments are made:

  \begin{itemize}

  \item
    Vintage data are grouped into: (1) \textless1960, (2) 1960--79,
    (3) 1980--99, (4) 2000s, (5) 2010s.
  \item
    Building Type data are grouped into: (1) Single-Family
    Detached, Single-Family Attached, and Mobile homes, and (2)
    Multifamily 2--4 units and Multifamily 5+ units.
  \item
    Climate zones are grouped into:
    \begin{itemize}
        \item 1A, 2A, 2B

\item 3A, 3B, 3C, 4B
\item 4A, 4C
\item 5A, 5B
\item6A, 6B and
\item 7A, 7B 7AK, 8AK.
  \end{itemize}
  \end{itemize}

  \begin{itemize}

  \item
    Federal Poverty Levels are progressively grouped together
    until all bins are combined.
  \item
    Tenure options are progressively grouped together until all
    bins are combined.
  \end{itemize}
\item
  Storm window saturations are based on D\&R International, Ltd. \href{https://www.energy.gov/sites/prod/files/2013/11/f5/residential_windows_coverings.pdf}{2013}.
 \textit{Residential Windows and Window Coverings: A Detailed
  View of the Installed Base and User Behavior}. Cut the \% storm windows by factor of 55\% because only 55\% of storms
  are installed year-round.
\item
  Due to lack of performance data, Triple-Pane windows with storms are
  modeled without the storm windows.
\item
  Due to lack of performance data, Double-Pane, Low-E, Non-Metal, Air,
  M-gain, and Exterior Clear Storm windows are modeled as Double-Pane,
  Clear, Non-Metal, Air, Exterior Clear Storm windows.
\end{itemize}
