\begin{customLongTable}{ |p{3cm}|p{1.25cm}|p{1.5cm}|p{1.5cm}|p{3cm}|p{3.5cm}| }
{The ResStock argument definitions set in the Eaves characteristic} {table:hc_arg_def_eaves}
{Name & Required & Units & Type & Choices & Description}
\texttt{geometry\_eaves\_depth} & true & ft & Double &  & The eaves depth of the roof.  \\ \hline
\texttt{overhangs\_front\_depth} & true & ft & Double &  & The depth of overhangs for windows for the front facade.  \\ \hline
\texttt{overhangs\_front\_distance\_to\_top\_of\_window} & true & ft & Double &  & The overhangs distance to the top of window for the front facade.  \\ \hline
\texttt{overhangs\_front\_distance\_to\_bottom\_of\_window} & true & ft & Double &  & The overhangs distance to the bottom of window for the front facade.  \\ \hline
\texttt{overhangs\_back\_depth} & true & ft & Double &  & The depth of overhangs for windows for the back facade.  \\ \hline
\texttt{overhangs\_back\_distance\_to\_top\_of\_window} & true & ft & Double &  & The overhangs distance to the top of window for the back facade.  \\ \hline
\texttt{overhangs\_back\_distance\_to\_bottom\_of\_window} & true & ft & Double &  & The overhangs distance to the bottom of window for the back facade.  \\ \hline
\texttt{overhangs\_left\_depth} & true & ft & Double &  & The depth of overhangs for windows for the left facade.  \\ \hline
\texttt{overhangs\_left\_distance\_to\_top\_of\_window} & true & ft & Double &  & The overhangs distance to the top of window for the left facade.  \\ \hline
\texttt{overhangs\_left\_distance\_to\_bottom\_of\_window} & true & ft & Double &  & The overhangs distance to the bottom of window for the left facade.  \\ \hline
\texttt{overhangs\_right\_depth} & true & ft & Double &  & The depth of overhangs for windows for the right facade.  \\ \hline
\texttt{overhangs\_right\_distance\_to\_top\_of\_window} & true & ft & Double &  & The overhangs distance to the top of window for the right facade.  \\ \hline
\texttt{overhangs\_right\_distance\_to\_bottom\_of\_window} & true & ft & Double &  & The overhangs distance to the bottom of window for the right facade.  \\
\end{customLongTable}
