\begin{customLongTable}{ |p{3cm}|p{1.25cm}|p{1.5cm}|p{1.5cm}|p{3cm}|p{3.5cm}| }
{The ResStock argument definitions set in the Hot Water Distribution characteristic} {table:hc_arg_def_hot_water_distribution}
{Name & Required & Units & Type & Choices & Description}
\texttt{hot\_water\_distribution\_system\_type} & true &  & Choice & Standard, Recirculation & The type of the hot water distribution system.  \\ \hline
\texttt{hot\_water\_distribution\_standard\_piping\_length} & false & ft & Double & auto & If the distribution system is Standard, the length of the piping.   \\ \hline
\texttt{hot\_water\_distribution\_recirc\_control\_type} & false &  & Choice & auto, no control, timer, temperature, presence sensor demand control, manual demand control & If the distribution system is Recirculation, the type of hot water recirculation control, if any.  \\ \hline
\texttt{hot\_water\_distribution\_recirc\_piping\_length} & false & ft & Double & auto & If the distribution system is Recirculation, the length of the recirculation piping.   \\ \hline
\texttt{hot\_water\_distribution\_recirc\_branch\_piping\_length} & false & ft & Double & auto & If the distribution system is Recirculation, the length of the recirculation branch piping.   \\ \hline
\texttt{hot\_water\_distribution\_recirc\_pump\_power} & false & W & Double & auto & If the distribution system is Recirculation, the recirculation pump power.   \\ \hline
\texttt{hot\_water\_distribution\_pipe\_r} & false & h-ft\textsuperscript{2}-R/Btu & Double & auto & Nominal R-value of the pipe insulation.   \\ \hline
\texttt{dwhr\_facilities\_connected} & true &  & Choice & none, one, all & Which facilities are connected for the drain water heat recovery. Use 'none' if there is no drain water heat recovery system.  \\ \hline
\texttt{dwhr\_equal\_flow} & false &  & Boolean & auto, true, false & Whether the drain water heat recovery has equal flow.  \\ \hline
\texttt{dwhr\_efficiency} & false & Frac & Double &  & The efficiency of the drain water heat recovery.  \\
\end{customLongTable}
