\begin{customLongTable}{ |p{3cm}|p{1.25cm}|p{1.5cm}|p{1.5cm}|p{3cm}|p{3.5cm}| }
{The ResStock argument definitions set in the HVAC Cooling Efficiency characteristic} {table:hc_arg_def_hvac_cooling_efficiency}
{Name & Required & Units & Type & Choices & Description}
\texttt{cooling\_system\_type} & true &  & Choice & none, central air conditioner, room air conditioner, evaporative cooler, mini-split, packaged terminal air conditioner & The type of cooling system. Use 'none' if there is no cooling system or if there is a heat pump serving a cooling load.  \\ \hline
\texttt{cooling\_system\_cooling\_efficiency\_type} & true &  & Choice & SEER, SEER2, EER, CEER & The efficiency type of the cooling system. System types central air conditioner and mini-split use SEER or SEER2. System types room air conditioner and packaged terminal air conditioner use EER or CEER. Ignored for system type evaporative cooler.  \\ \hline
\texttt{cooling\_system\_cooling\_efficiency} & true &  & Double &  & The rated efficiency value of the cooling system. Ignored for evaporative cooler.  \\ \hline
\texttt{cooling\_system\_cooling\_capacity} & false & Btu/hr & Double &  & The output cooling capacity of the cooling system.   \\ \hline
\texttt{cooling\_system\_cooling\_autosizing\_limit} & false & Btu/hr & Double &  & The maximum capacity limit applied to the auto-sizing methodology.   \\ \hline
\texttt{cooling\_system\_is\_ducted} & false &  & Boolean & auto, true, false & Whether the cooling system is ducted or not. Only used for mini-split and evaporative cooler. It's assumed that central air conditioner is ducted, and room air conditioner and packaged terminal air conditioner are not ducted.  \\ \hline
\texttt{cooling\_system\_compressor\_type} & false &  & Choice & auto, single stage, two stage, variable speed & The compressor type of the cooling system. Required for central air conditioner and mini-split.  \\ \hline
\texttt{cooling\_system\_crankcase\_heater\_watts} & false & W & Double & auto & Cooling system crankcase heater power consumption in Watts. Applies only to central air conditioner, room air conditioner, packaged terminal air conditioner and mini-split.   \\ \hline
\texttt{cooling\_system\_integrated\_heating\_system\_capacity} & false & Btu/hr & Double &  & The output heating capacity of the heating system integrated into cooling system.   \\ \hline
\texttt{cooling\_system\_integrated\_heating\_system\_efficiency\_percent} & false & Frac & Double &  & The rated heating efficiency value of the heating system integrated into cooling system. Only used for packaged terminal air conditioner and room air conditioner.  \\ \hline
\texttt{cooling\_system\_integrated\_heating\_system\_fraction\_heat\_load\_served} & false & Frac & Double &  & The heating load served by the heating system integrated into cooling system. Only used for packaged terminal air conditioner and room air conditioner.  \\ \hline
\texttt{cooling\_system\_integrated\_heating\_system\_fuel} & false &  & Choice & auto, electricity, natural gas, fuel oil, propane, wood, wood pellets, coal & The fuel type of the heating system integrated into cooling system. Only used for packaged terminal air conditioner and room air conditioner.  \\
\end{customLongTable}
