\begin{customLongTable}{ |p{3cm}|p{1.25cm}|p{1.5cm}|p{1.5cm}|p{3cm}|p{3.5cm}| }
{The ResStock argument definitions set in the HVAC Heating Efficiency characteristic} {table:hc_arg_def_hvac_heating_efficiency}
{Name & Required & Units & Type & Choices & Description}
\texttt{heating\_system\_type} & true &  & Choice & none, Furnace, WallFurnace, FloorFurnace, Boiler, ElectricResistance, Stove, SpaceHeater, Fireplace, Shared Boiler w/ Baseboard, Shared Boiler w/ Ductless Fan Coil & The type of heating system. Use 'none' if there is no heating system or if there is a heat pump serving a heating load.  \\ \hline
\texttt{heating\_system\_heating\_efficiency} & true & Frac & Double &  & The rated heating efficiency value of the heating system.  \\ \hline
\texttt{heating\_system\_heating\_capacity} & false & Btu/hr & Double &  & The output heating capacity of the heating system.   \\ \hline
\texttt{heating\_system\_heating\_autosizing\_limit} & false & Btu/hr & Double &  & The maximum capacity limit applied to the auto-sizing methodology.   \\ \hline
\texttt{heating\_system\_fraction\_heat\_load\_served} & true & Frac & Double &  & The heating load served by the heating system.  \\ \hline
\texttt{heating\_system\_has\_flue\_or\_chimney} & true &  & String &  & Whether the heating system has a flue or chimney.  \\ \hline
\texttt{heat\_pump\_type} & true &  & Choice & none, air-to-air, mini-split, ground-to-air, packaged terminal heat pump, room air conditioner with reverse cycle & The type of heat pump. Use 'none' if there is no heat pump.  \\ \hline
\texttt{heat\_pump\_heating\_efficiency\_type} & true &  & Choice & HSPF, HSPF2, COP & The heating efficiency type of heat pump. System types air-to-air and mini-split use HSPF or HSPF2. System types ground-to-air, packaged terminal heat pump and room air conditioner with reverse cycle use COP.  \\ \hline
\texttt{heat\_pump\_heating\_efficiency} & true &  & Double &  & The rated heating efficiency value of the heat pump.  \\ \hline
\texttt{heat\_pump\_cooling\_efficiency\_type} & true &  & Choice & SEER, SEER2, EER, CEER & The cooling efficiency type of heat pump. System types air-to-air and mini-split use SEER or SEER2. System types ground-to-air, packaged terminal heat pump and room air conditioner with reverse cycle use EER.  \\ \hline
\texttt{heat\_pump\_cooling\_efficiency} & true &  & Double &  & The rated cooling efficiency value of the heat pump.  \\ \hline
\texttt{heat\_pump\_sizing\_methodology} & false &  & Choice & auto, ACCA, HERS, MaxLoad & The auto-sizing methodology to use when the heat pump capacity is not provided.   \\ \hline
\texttt{heat\_pump\_sizing\_is\_duct\_limited} & false &  & Boolean & true, false & Whether the (ducted) heat pump has an upper limit for autosized heating/cooling capacity and an adjusted blower fan efficiency (W/CFM) value. This argument is only applicable for heat pump upgrades.  \\ \hline
\texttt{heat\_pump\_backup\_sizing\_methodology} & false &  & Choice & auto, emergency, supplemental & The auto-sizing methodology to use when the heat pump backup capacity is not provided.   \\ \hline
\texttt{heat\_pump\_heating\_capacity} & false & Btu/hr & Double &  & The output heating capacity of the heat pump.   \\ \hline
\texttt{heat\_pump\_heating\_autosizing\_limit} & false & Btu/hr & Double &  & The maximum capacity limit applied to the auto-sizing methodology.   \\ \hline
\texttt{heat\_pump\_fraction\_heat\_load\_served} & true & Frac & Double &  & The heating load served by the heat pump.  \\ \hline
\texttt{heat\_pump\_cooling\_capacity} & false & Btu/hr & Double &  & The output cooling capacity of the heat pump.   \\ \hline
\texttt{heat\_pump\_cooling\_autosizing\_limit} & false & Btu/hr & Double &  & The maximum capacity limit applied to the auto-sizing methodology.   \\ \hline
\texttt{heat\_pump\_fraction\_cool\_load\_served} & true & Frac & Double &  & The cooling load served by the heat pump.  \\ \hline
\texttt{heat\_pump\_backup\_use\_existing\_system} & false &  & Boolean & true, false & Whether the heat pump uses the existing heating system as backup. If true and backup type of the heat pump is 'integrated', heat_pump_backup_xxx arguments are assigned values based on the existing heating system. If true and backup type of the heat pump is 'separate', heating_system_2_xxx arguments are assigned values based on the existing heating system. This argument is only applicable for heat pump upgrades.  \\ \hline
\texttt{heat\_pump\_backup\_type} & true &  & Choice & auto, none, integrated, separate & The backup type of the heat pump. If 'integrated', represents e.g. built-in electric strip heat or dual-fuel integrated furnace. If 'separate', represents e.g. electric baseboard or boiler based on the Heating System 2 specified below. Use 'none' if there is no backup heating. E.g., 'integrated' or 'auto'. Use 'auto' when Backup Use Existing System is true.  \\ \hline
\texttt{heat\_pump\_backup\_fuel} & true &  & Choice & auto, electricity, natural gas, fuel oil, propane & The backup fuel type of the heat pump. Only applies if Backup Type is 'integrated'. E.g., 'electricity' or 'auto'. Use 'auto' when Backup Use Existing System is true.  \\ \hline
\texttt{heat\_pump\_backup\_heating\_efficiency} & true &  & Double & auto & The backup rated efficiency value of the heat pump. Percent for electricity fuel type. AFUE otherwise. Only applies if Backup Type is 'integrated'. E.g., '1' or 'auto'. Use 'auto' when Backup Use Existing System is true.  \\ \hline
\texttt{heat\_pump\_backup\_heating\_capacity} & false & Btu/hr & Double &  & The backup output heating capacity of the heat pump.   \\ \hline
\texttt{heat\_pump\_backup\_heating\_autosizing\_limit} & false & Btu/hr & Double &  & The maximum capacity limit applied to the auto-sizing methodology if Backup Type is 'integrated'.   \\ \hline
\texttt{heat\_pump\_heating\_capacity\_fraction\_17\_f} & false & Frac & Double & auto & The output heating capacity of the heat pump at 17F divided by the above nominal heating capacity at 47F. Applies to all heat pump types except ground-to-air.   \\ \hline
\texttt{heat\_pump\_is\_ducted} & false &  & Boolean & auto, true, false & Whether the heat pump is ducted or not. Only used for mini-split. It's assumed that air-to-air and ground-to-air are ducted, and packaged terminal heat pump and room air conditioner with reverse cycle are not ducted.   \\ \hline
\texttt{heat\_pump\_backup\_heating\_lockout\_temp} & false & F & Double & auto & The temperature above which the heat pump backup system is disabled. If both this and Compressor Lockout Temperature are provided and use the same value, it essentially defines a switchover temperature (for, e.g., a dual-fuel heat pump). Applies for both Backup Type of 'integrated' and 'separate'.   \\ \hline
\texttt{heat\_pump\_compressor\_lockout\_temp} & false & F & Double & auto & The temperature below which the heat pump compressor is disabled. If both this and Backup Heating Lockout Temperature are provided and use the same value, it essentially defines a switchover temperature (for, e.g., a dual-fuel heat pump). Applies to all heat pump types other than ground-to-air.   \\ \hline
\texttt{heat\_pump\_compressor\_type} & false &  & Choice & auto, single stage, two stage, variable speed & The compressor type of the heat pump. Required for air-to-air, mini-split and ground-to-air.  \\ \hline
\texttt{heat\_pump\_crankcase\_heater\_watts} & false & W & Double & auto & Heat Pump crankcase heater power consumption in Watts. Applies only to air-to-air, mini-split, packaged terminal heat pump and room air conditioner with reverse cycle.   \\ \hline
\texttt{heat\_pump\_pan\_heater\_watts} & false & W & Double & auto & Heat Pump pan heater power consumption in Watts. Applies only to air-to-air and mini-split.   \\ \hline
\texttt{heat\_pump\_pan\_heater\_control\_type} & false &  & Choice & auto, continuous, defrost mode & Heat pump pan heater control type. If 'continuous', operates continuously when outdoor temperature is below 32F. If 'defrost mode', operates only during defrost mode when outdoor temperature is below 32F. Applies only to air-to-air and mini-split.   \\ \hline
\texttt{geothermal\_loop\_configuration} & false &  & Choice & auto, none, vertical & Configuration of the geothermal loop. Only applies to ground-to-air heat pump type.   \\ \hline
\texttt{geothermal\_loop\_borefield\_configuration} & false &  & Choice & auto, Rectangle, Open Rectangle, C, L, U, Lopsided U & Borefield configuration of the geothermal loop. Only applies to ground-to-air heat pump type.   \\ \hline
\texttt{geothermal\_loop\_loop\_flow} & false & gpm & Double &  & Water flow rate through the geothermal loop. Only applies to ground-to-air heat pump type.   \\ \hline
\texttt{geothermal\_loop\_boreholes\_count} & false & \# & Integer &  & Number of boreholes. Only applies to ground-to-air heat pump type.   \\ \hline
\texttt{geothermal\_loop\_boreholes\_length} & false & ft & Double &  & Average length of each borehole (vertical). Only applies to ground-to-air heat pump type.   \\ \hline
\texttt{geothermal\_loop\_boreholes\_spacing} & false & ft & Double & auto & Distance between bores. Only applies to ground-to-air heat pump type.   \\ \hline
\texttt{geothermal\_loop\_boreholes\_diameter} & false & in & Double & auto & Diameter of bores. Only applies to ground-to-air heat pump type.   \\ \hline
\texttt{geothermal\_loop\_grout\_type} & false &  & Choice & auto, standard, thermally enhanced & Grout type of the geothermal loop. Only applies to ground-to-air heat pump type.   \\ \hline
\texttt{geothermal\_loop\_pipe\_type} & false &  & Choice & auto, standard, thermally enhanced & Pipe type of the geothermal loop. Only applies to ground-to-air heat pump type.   \\ \hline
\texttt{geothermal\_loop\_pipe\_diameter} & false & in & Choice & auto, 3/4" pipe, 1" pipe, 1-1/4" pipe & Pipe diameter of the geothermal loop. Only applies to ground-to-air heat pump type.   \\ \hline
\texttt{heating\_system\_pilot\_light} & false & Btuh & Double &  & The fuel usage of the pilot light. Applies only to Furnace, WallFurnace, FloorFurnace, Stove, Boiler, and Fireplace with non-electric fuel type.   \\ \hline
\texttt{simulation\_control\_ground\_to\_air\_heat\_pump\_model\_type} & false &  & Choice & auto, standard, experimental & Research feature to select the type of ground-to-air heat pump model. Use standard for standard ground-to-air heat pump modeling. Use experimental for an improved model that better accounts for coil staging.   \\
\end{customLongTable}
