\begin{customLongTable}{ |p{3cm}|p{1.25cm}|p{1.5cm}|p{1.5cm}|p{3cm}|p{3.5cm}| }
{The ResStock argument definitions set in the Insulation Foundation Wall characteristic} {table:hc_arg_def_insulation_foundation_wall}
{Name & Required & Units & Type & Choices & Description}
\texttt{foundation\_wall\_type} & false &  & Choice & auto, solid concrete, concrete block, concrete block foam core, concrete block perlite core, concrete block vermiculite core, concrete block solid core, double brick, wood & The material type of the foundation wall.   \\ \hline
\texttt{foundation\_wall\_thickness} & false & in & Double & auto & The thickness of the foundation wall.   \\ \hline
\texttt{foundation\_wall\_insulation\_r} & true & h-ft\textsuperscript{2}-R/Btu & Double &  & Nominal R-value for the foundation wall insulation. Only applies to basements/crawlspaces.  \\ \hline
\texttt{foundation\_wall\_insulation\_location} & false & ft & Choice & auto, interior, exterior & Whether the insulation is on the interior or exterior of the foundation wall. Only applies to basements/crawlspaces.  \\ \hline
\texttt{foundation\_wall\_insulation\_distance\_to\_top} & false & ft & Double & auto & The distance from the top of the foundation wall to the top of the foundation wall insulation. Only applies to basements/crawlspaces.   \\ \hline
\texttt{foundation\_wall\_insulation\_distance\_to\_bottom} & false & ft & Double & auto & The distance from the top of the foundation wall to the bottom of the foundation wall insulation. Only applies to basements/crawlspaces.   \\ \hline
\texttt{foundation\_wall\_assembly\_r} & false & h-ft\textsuperscript{2}-R/Btu & Double &  & Assembly R-value for the foundation walls. Only applies to basements/crawlspaces. If provided, overrides the previous foundation wall insulation inputs.   \\
\end{customLongTable}
