\begin{customLongTable}{ |p{3cm}|p{1.5cm}|p{1.5cm}|p{1.5cm}|p{3cm}|p{3.5cm}| }
{The ResStock argument definitions set in the Lighting characteristic} {table:hc_arg_def_lighting}
{Name & Required & Units & Type & Choices & Description}
\texttt{lighting\_present} & true &  & Boolean & true, false & Whether there is lighting energy use.  \\ \hline
\texttt{lighting\_interior\_fraction\_cfl} & true &  & Double &  & Fraction of all lamps (interior) that are compact fluorescent. Lighting not specified as CFL, LFL, or LED is assumed to be incandescent.  \\ \hline
\texttt{lighting\_interior\_fraction\_lfl} & true &  & Double &  & Fraction of all lamps (interior) that are linear fluorescent. Lighting not specified as CFL, LFL, or LED is assumed to be incandescent.  \\ \hline
\texttt{lighting\_interior\_fraction\_led} & true &  & Double &  & Fraction of all lamps (interior) that are light emitting diodes. Lighting not specified as CFL, LFL, or LED is assumed to be incandescent.  \\ \hline
\texttt{lighting\_exterior\_fraction\_cfl} & true &  & Double &  & Fraction of all lamps (exterior) that are compact fluorescent. Lighting not specified as CFL, LFL, or LED is assumed to be incandescent.  \\ \hline
\texttt{lighting\_exterior\_fraction\_lfl} & true &  & Double &  & Fraction of all lamps (exterior) that are linear fluorescent. Lighting not specified as CFL, LFL, or LED is assumed to be incandescent.  \\ \hline
\texttt{lighting\_exterior\_fraction\_led} & true &  & Double &  & Fraction of all lamps (exterior) that are light emitting diodes. Lighting not specified as CFL, LFL, or LED is assumed to be incandescent.  \\ \hline
\texttt{lighting\_garage\_fraction\_cfl} & true &  & Double &  & Fraction of all lamps (garage) that are compact fluorescent. Lighting not specified as CFL, LFL, or LED is assumed to be incandescent.  \\ \hline
\texttt{lighting\_garage\_fraction\_lfl} & true &  & Double &  & Fraction of all lamps (garage) that are linear fluorescent. Lighting not specified as CFL, LFL, or LED is assumed to be incandescent.  \\ \hline
\texttt{lighting\_garage\_fraction\_led} & true &  & Double &  & Fraction of all lamps (garage) that are light emitting diodes. Lighting not specified as CFL, LFL, or LED is assumed to be incandescent.  \\
\end{customLongTable}
