\begin{customLongTable}{ |p{3cm}|p{1.5cm}|p{1.5cm}|p{1.5cm}|p{3cm}|p{3.5cm}| }
{The ResStock argument definitions set in the Mechanical Ventilation characteristic} {table:hc_arg_def_mechanical ventilation}
{Name & Required & Units & Type & Choices & Description}
\texttt{mech\_vent\_fan\_type} & true &  & Choice & none, exhaust only, supply only, energy recovery ventilator, heat recovery ventilator, balanced, central fan integrated supply & The type of the mechanical ventilation. Use 'none' if there is no mechanical ventilation system.  \\ \hline
\texttt{mech\_vent\_flow\_rate} & false & CFM & Double & auto & The flow rate of the mechanical ventilation.   \\ \hline
\texttt{mech\_vent\_hours\_in\_operation} & false & hrs/day & Double & auto & The hours in operation of the mechanical ventilation.   \\ \hline
\texttt{mech\_vent\_recovery\_efficiency\_type} & true &  & Choice & Unadjusted, Adjusted & The total recovery efficiency type of the mechanical ventilation.  \\ \hline
\texttt{mech\_vent\_total\_recovery\_efficiency} & true & Frac & Double &  & The Unadjusted or Adjusted total recovery efficiency of the mechanical ventilation. Applies to energy recovery ventilator.  \\ \hline
\texttt{mech\_vent\_sensible\_recovery\_efficiency} & true & Frac & Double &  & The Unadjusted or Adjusted sensible recovery efficiency of the mechanical ventilation. Applies to energy recovery ventilator and heat recovery ventilator.  \\ \hline
\texttt{mech\_vent\_fan\_power} & false & W & Double & auto & The fan power of the mechanical ventilation.   \\ \hline
\texttt{mech\_vent\_num\_units\_served} & true & \# & Integer &  & Number of dwelling units served by the mechanical ventilation system. Must be 1 if single-family detached. Used to apportion flow rate and fan power to the unit.  \\ \hline
\texttt{mech\_vent\_2\_fan\_type} & true &  & Choice & none, exhaust only, supply only, energy recovery ventilator, heat recovery ventilator, balanced & The type of the second mechanical ventilation. Use 'none' if there is no second mechanical ventilation system.  \\ \hline
\texttt{mech\_vent\_2\_flow\_rate} & true & CFM & Double &  & The flow rate of the second mechanical ventilation.  \\ \hline
\texttt{mech\_vent\_2\_hours\_in\_operation} & true & hrs/day & Double &  & The hours in operation of the second mechanical ventilation.  \\ \hline
\texttt{mech\_vent\_2\_recovery\_efficiency\_type} & true &  & Choice & Unadjusted, Adjusted & The total recovery efficiency type of the second mechanical ventilation.  \\ \hline
\texttt{mech\_vent\_2\_total\_recovery\_efficiency} & true & Frac & Double &  & The Unadjusted or Adjusted total recovery efficiency of the second mechanical ventilation. Applies to energy recovery ventilator.  \\ \hline
\texttt{mech\_vent\_2\_sensible\_recovery\_efficiency} & true & Frac & Double &  & The Unadjusted or Adjusted sensible recovery efficiency of the second mechanical ventilation. Applies to energy recovery ventilator and heat recovery ventilator.  \\ \hline
\texttt{mech\_vent\_2\_fan\_power} & true & W & Double &  & The fan power of the second mechanical ventilation.  \\ \hline
\texttt{whole\_house\_fan\_present} & true &  & Boolean & true, false & Whether there is a whole house fan.  \\ \hline
\texttt{whole\_house\_fan\_flow\_rate} & false & CFM & Double & auto & The flow rate of the whole house fan.   \\ \hline
\texttt{whole\_house\_fan\_power} & false & W & Double & auto & The fan power of the whole house fan.   \\ \hline
\texttt{mech\_vent\_shared\_frac\_recirculation} & false & Frac & Double &  & Fraction of the total supply air that is recirculated, with the remainder assumed to be outdoor air. The value must be 0 for exhaust only systems. Required for a shared mechanical ventilation system.  \\ \hline
\texttt{mech\_vent\_shared\_precooling\_efficiency} & false & COP & Double &  & Efficiency of the preconditioning cooling equipment. Only used for a shared mechanical ventilation system.   \\ \hline
\texttt{mech\_vent\_shared\_precooling\_fraction\_cool\_load\_served} & false & Frac & Double &  & Fraction of cooling load introduced by the shared ventilation system that is met by the preconditioning cooling equipment.   \\ \hline
\texttt{mech\_vent\_shared\_precooling\_fuel} & false &  & Choice & auto, electricity & Fuel type of the preconditioning cooling equipment. Only used for a shared mechanical ventilation system.   \\ \hline
\texttt{mech\_vent\_shared\_preheating\_efficiency} & false & COP & Double &  & Efficiency of the preconditioning heating equipment. Only used for a shared mechanical ventilation system.   \\ \hline
\texttt{mech\_vent\_shared\_preheating\_fraction\_heat\_load\_served} & false & Frac & Double &  & Fraction of heating load introduced by the shared ventilation system that is met by the preconditioning heating equipment.   \\ \hline
\texttt{mech\_vent\_shared\_preheating\_fuel} & false &  & Choice & auto, electricity, natural gas, fuel oil, propane, wood, wood pellets, coal & Fuel type of the preconditioning heating equipment. Only used for a shared mechanical ventilation system.   \\
\end{customLongTable}
