\begin{customLongTable}{ |p{3cm}|p{1.5cm}|p{1.5cm}|p{1.5cm}|p{3cm}|p{3.5cm}| }
{The ResStock argument definitions set in the Window Areas characteristic} {table:hc_arg_def_window areas}
{Name & Required & Units & Type & Choices & Description}
\texttt{window\_front\_wwr} & true & Frac & Double &  & The ratio of window area to wall area for the unit's front facade. Enter 0 if specifying Front Window Area instead. If the front wall is adiabatic, the value will be ignored.  \\ \hline
\texttt{window\_back\_wwr} & true & Frac & Double &  & The ratio of window area to wall area for the unit's back facade. Enter 0 if specifying Back Window Area instead. If the back wall is adiabatic, the value will be ignored.  \\ \hline
\texttt{window\_left\_wwr} & true & Frac & Double &  & The ratio of window area to wall area for the unit's left facade (when viewed from the front). Enter 0 if specifying Left Window Area instead. If the left wall is adiabatic, the value will be ignored.  \\ \hline
\texttt{window\_right\_wwr} & true & Frac & Double &  & The ratio of window area to wall area for the unit's right facade (when viewed from the front). Enter 0 if specifying Right Window Area instead. If the right wall is adiabatic, the value will be ignored.  \\ \hline
\texttt{window\_area\_front} & true & ft^2 & Double &  & The amount of window area on the unit's front facade. Enter 0 if specifying Front Window-to-Wall Ratio instead. If the front wall is adiabatic, the value will be ignored.  \\ \hline
\texttt{window\_area\_back} & true & ft^2 & Double &  & The amount of window area on the unit's back facade. Enter 0 if specifying Back Window-to-Wall Ratio instead. If the back wall is adiabatic, the value will be ignored.  \\ \hline
\texttt{window\_area\_left} & true & ft^2 & Double &  & The amount of window area on the unit's left facade (when viewed from the front). Enter 0 if specifying Left Window-to-Wall Ratio instead. If the left wall is adiabatic, the value will be ignored.  \\ \hline
\texttt{window\_area\_right} & true & ft^2 & Double &  & The amount of window area on the unit's right facade (when viewed from the front). Enter 0 if specifying Right Window-to-Wall Ratio instead. If the right wall is adiabatic, the value will be ignored.  \\ \hline
\texttt{window\_aspect\_ratio} & true & Frac & Double &  & Ratio of window height to width.  \\ \hline
\texttt{skylight\_area\_front} & true & ft^2 & Double &  & The amount of skylight area on the unit's front conditioned roof facade.  \\ \hline
\texttt{skylight\_area\_back} & true & ft^2 & Double &  & The amount of skylight area on the unit's back conditioned roof facade.  \\ \hline
\texttt{skylight\_area\_left} & true & ft^2 & Double &  & The amount of skylight area on the unit's left conditioned roof facade (when viewed from the front).  \\ \hline
\texttt{skylight\_area\_right} & true & ft^2 & Double &  & The amount of skylight area on the unit's right conditioned roof facade (when viewed from the front).  \\
\end{customLongTable}
