\begin{itemize}
\item Check the assumptions on the source tsv files.
\item If a house has a wall furnace with fuel other than natural_gas, efficiency level based on natural_gas from expanded_HESC_HVAC_efficiencies.tsv is assigned.
\item If a house has a heat pump with fuel other than electricity (presumed dual-fuel heat pump), the heating type is assumed to be furnace and not heat pump.
\item The shipment volume for boiler was not available, so shipment volume for furnace in furnace-shipments-table.tsv was used instead.
\item Due to low sample size for some categories, the HVAC Has Shared System categories 'Cooling Only' and 'None' are combined for the purpose of querying Heating Efficiency distributions.
\item For 'other' heating system types, we assign them to Electric Baseboard if fuel is Electric, and assign them to Wall/Floor Furnace if fuel is natural_gas, fuel_oil or propane.
\item For Other Fuel and Wood, the lowest efficiency systems are assumed.
\item For Alaska, we are using a field in ARIS that lumps multi-family 2-4 units and multi-family 5+ units buildings together. Data from the American Community Survey is used to distribute the between these two building types.
\item For Alaska, electric space heaters are modeled as electric baseboards.
\item For Alaska, Toyo/monitor direct-vent devices and other fuel space heaters are not modeled.
\item For Alaska, fireplace and stoves are not modeled.
\item For Alaska, all heat pumps (including geothermal) are assumed to be non-ducted air source heat pumps.
\end{itemize}
