\begin{itemize}
\item Wood and Vinyl are considered same material
\item Triple Pane assumed to be 100\% low-e
\item Only breaking out clear and low-e windows for the Double, Non-Metal frame type
\item Source of low-e distribution is based on engineering judgement, informed by high-levelsales trends observed in Ducker Worldwide studies of the U.S.~Market for Windows, Doors and Skylights.
\item Due to low sample sizes, the following adjustments are made:
  \begin{itemize}
  \item Vintage data are grouped into: 1) <1960, 2) 1960-79, 3) 1980-99, 4) 2000s, 5) 2010s.
  \item Building Type data are grouped into: 1) Single-Family Detached, Single-Family Attached, and Mobile homes and 2) Multi-Family 2-4 units and Multi-Family 5+ units.
  \item Climate zones are grouped into: 1) 1A, 2A, 2B
  \end{itemize}
\item 2) 3A, 3B, 3C, 4B
\item 3) 4A, 4C
\item 4) 5A, 5B
\item 5) 6A, 6B
\item and 6) 7A, 7B 7AK, 8AK.
  \begin{itemize}
  \item Federal Poverty Levels are progressively grouped together until all bins are combined.
  \item Tenure options are progressively grouped together until all bins are combined.
  \end{itemize}
\item Storm window saturations are based on D\&R International, Ltd. 'Residential Windows and Window Coverings: A Detailed View of the Installed Base and User Behavior' 2013. \href{https://www.energy.gov/sites/prod/files/2013/11/f5/residential_windows_coverings.pdf}{https://www.energy.gov/sites/prod/files/2013/11/f5/residential\_windows\_coverings.pdf}. Cut the \% storm windows by factor of 55\% because only 55\% of storms are installed year round
\item Due to lack of performance data storm windows with triple-pane are modeled without the storm windows
\item Due to lack of performance data Double-pane, Low-E, Non-Metal, Air, M-gain, Exterior Clear Storm windows are modeled as Double-pane, Clear, Non-Metal, Air, Exterior Clear Storm windows
\end{itemize}
