\chapter{Housing Characteristics and Inputs} \label{sec:resstock_inputs}

In this section, we overview each of the input housing characteristics for ResStock in detail including options and associated properties. In ResStock, each input characteristic gets its own input file. The full set of housing characteristic input files is available in the main \href{https://github.com/NREL/resstock/releases/tag/2025_Release_1}{ResStock GitHub repository} in the project national folder. We discuss each of these input files as well as the general theory for how different systems and components are modeled. Within each section we also provide the national-level stock saturation of each option within a characteristic. These top-level saturations collapse much of the detail and nuance in ResStock's probability distributions, but the saturations serve to give a sense of how common different options are, generally, in the United States.

We organize this discussion by the major types of inputs: Geography, Geometry, Envelope, HVAC, Water Heating, Appliances, Lighting, Plug Loads, and Household characteristics. For each of these major sections, we discuss ResStock's approach to these input types, highlighting where it might vary from OS-HPXML. Additionally, we discuss weather inputs to ResStock, which is specified separately from the main input files.

\section{Geography}
ResStock provides a wide range of geographic inputs and outputs. These fields allow for detailed input probability distributions for the U.S.~residential building stock characterization. These geography fields are also useful for aggregating and analyzing ResStock outputs.

All the geography fields are compiled into a geography lookup table that contains census block-level resolution. For reference, the Geography Hierarchy Diagram for Census geographies can be found on the \href{https://www2.census.gov/geo/pdfs/reference/geodiagram.pdf}{Geography Hierarchy Diagram} U.S.~Census website. This diagram shows that the fundamental geography is a census block. All other census geographies stem from this definition. This hierarchy is used to create a lookup table for all geography characteristics in ResStock.

Added to this table are occupied and vacant unit counts for each census block from the \href{https://www.census.gov/programs-surveys/decennial-census/about/rdo.html}{2020 U.S.~Census Redistricting Data} and ACS 5-year 2016 data. The ACS number of units is specified by census tract and downscaled to the census block level using the 2020 Redistricting data. The 2020 census block data are converted to 2010 census blocks using the National Historical Geographic Information System (NHGIS) \href{https://www.nhgis.org/geographic-crosswalks}{Geographic Crosswalks}. All the characteristics and distributions of housing characteristics are pivoted from this lookup table relating the geography definitions and housing unit counts. Also in this lookup file is the NHGIS GISJOIN codes that help join this file to other geography fields not in the lookup table or the ResStock outputs.

The ACS housing unit data are typically used by ResStock to specify in the project file the number of housing units in the United States. The ACS data are a 5-year average compared to the single-year 2020 Redistricting data. Consistency for using ACS for unit counts at the census geographies is also achieved except for the ``City'' characteristic. The City characteristic uses the downscaled data from the ACS to census block, because City boundaries are specified by census blocks.

The census geographies are set to be consistent with the U.S.~Census Bureau's definitions as of July 1, 2015. The 2010 Census geography definitions and changes between the 2010 Census and July 1, 2015, can be found on the \href{https://www.census.gov/programs-surveys/decennial-census/decade.html}{U.S.~Census Bureau Decennial Census} website.

When looking at the structure of the Geography dependencies, the ASHRAE IECC 2004 input file does not have any dependencies. ASHRAE IECC 2004 is the top-level geography characteristic. The reason this climate zone characteristic is first and not some U.S.~Census characteristic is because of the way the ResStock Sampling algorithm works. By using the large climate zones, more uniformity is achieved in the spatial allocation of the samples. From ASHRAE IECC climate zone, the County and Public Use Microdata Area (PUMA) characteristic is assigned, placing the sample in the smallest resolution geographic characteristic. From here the other geographic characteristics are various aggregations of the County and PUMA field or larger geographies.

In discussing the Geography inputs to ResStock, we break it down into four subcategories: Census Geographies, Climate Zones, Grid and Emissions Geographies, and Other Geographies.

\subsection{Census Geographies}
This section contains ResStock characteristics based on the U.S.~Census geographic definitions. There are 11 input files to ResStock that specify Census Geographies:
\begin{itemize}
    \item Census Region
    \item Census Division
    \item State
    \item County
    \item PUMA
    \item County and PUMA
    \item Metropolitan and Micropolitan Statistical Area
    \item City
    \item American Indian/Alaska Native/Native Hawaiian (AIANNH) Area
    \item County Metro Status
    \item PUMA Metro Status.
\end{itemize}

\subsubsection{Census Region}
\input{characteristics/Census Region}

\subsubsection{Census Division}
\input{characteristics/Census Division}

\subsubsection{State}
\input{characteristics/State}

\subsubsection{County}
\input{characteristics/County}

\subsubsection{Public Use Microdata Area}
\input{characteristics/PUMA}

\subsubsection{County and PUMA}
\input{characteristics/County and PUMA}

\subsubsection{Metropolitan and Micropolitan Statistical Area}
\input{characteristics/Metropolitan and Micropolitan Statistical Area}

\subsubsection{City}
\input{characteristics/City}

\subsubsection{AIANNH Area}
\input{characteristics/AIANNH Area}

\subsubsection{County Metro Status}
\input{characteristics/County Metro Status}

\subsubsection{PUMA Metro Status}
\input{characteristics/PUMA Metro Status}

\subsection{Climate Zones}
This section of ResStock characteristics is a set of climate zone definitions. There are five input files to ResStock that specify climate zones:
\begin{itemize}
    \item ASHRAE IECC Climate Zone 2004
    \item ASHRAE IECC Climate Zone 2004---Sub-CZ Split
    \item Building America Climate Zones
    \item California Energy Commission (CEC) Climate Zones
    \item ENERGY STAR\textsuperscript{\textregistered} Climate Zone 2023.
\end{itemize}

\subsubsection{ASHRAE IECC Climate Zone 2004} \label{sec:ashrae_2004_tsv}
\input{characteristics/ASHRAE IECC Climate Zone 2004}

\subsubsection{ASHRAE IECC Climate Zone 2004 -- Sub-CZ Split}
\input{characteristics/ASHRAE IECC Climate Zone 2004 - Sub-CZ Split}

\subsubsection{Building America Climate Zones}
\input{characteristics/Building America Climate Zone}

\subsubsection{California Energy Commission Climate Zones}
\input{characteristics/CEC Climate Zone}

\subsubsection{ENERGY STAR Climate Zone 2023}
\input{characteristics/Energystar Climate Zone 2023}

\subsection{Grid and Emissions Geographies}

In ResStock there are three input files describing geographies relevant to the electric grid and emissions calculations:

\begin{itemize}
    \item ReEDS Balancing Area
    \item Generation and Emissions Assessment (GEA) Region
    \item ISO RTO Region.
\end{itemize}

\subsubsection{ReEDS Balancing Area}
\input{characteristics/REEDS Balancing Area}

\subsubsection{Generation and Emissions Assessment (GEA) Region}
\input{characteristics/Generation and Emissions Assessment Region}

\subsubsection{ISO RTO Region}
\input{characteristics/ISO RTO Region}

\subsection{Other Geographies}

In this section, we cover other miscellaneous geographies in ResStock. This includes four input files:
\begin{itemize}
    \item Census Division RECS
    \item Custom State
    \item Location Region
    \item American Housing Survey Region.
\end{itemize}

\subsubsection{Census Division RECS}
\input{characteristics/Census Division RECS}

\subsubsection{Custom State}
\input{characteristics/Custom State}

\subsubsection{Location Region}
\input{characteristics/Location Region}

\subsubsection{American Housing Survey Region}
\input{characteristics/AHS Region}

\subsection{Weather Data}
Weather data are closely related to the specification of geography inputs, since weather varies by location. In ResStock, weather data are not specified in the Housing Characteristics input data like most things, but are specified as their own set of input files. In ResStock, weather files are specified at the county level, although sometimes adjacent counties share the same weather files.

As is standard in most building energy models, ResStock can be run with either Typical Meteorological Year (TMY) or Actual Meteorological Year (AMY) data. Hypothetically, ResStock could be run with any other weather data in EPW format, but all data releases to date have been based upon TMY or AMY data. TMY are synthetically constructed files based upon historic weather where each month of the year is picked from the most representative (i.e., ``typical'') real month from the previous 30 years (\cite{Wilcox2008}). This has the advantage of avoiding extreme or unusual weather, and can be appropriate for analyses that aggregate annual energy use. However, TMY files, by design, will not capture worst-case or extreme situations. Also, given that TMYs are constructed upon historical weather, it is unlikely they truly represent what is ``typical'' for a location given the reality of accelerating climate change. ``Typical'' is a moving target, and what was typical 10 years ago is less likely to be typical today. Furthermore, TMY has the disadvantage that adjacent weather stations might not use the same historical years for the same months. For example, a TMY in Denver, CO, might use 2012 for the July file, but 30 miles (40 kilometers) away, the Boulder, CO, TMY station might use 1999 for July. This misalignment of weather years can lead to modeling of non-coincident temporal energy use in ResStock and will likely lead to the underrepresentation of electricity peaks when considering geographies spread across more than one weather file.

AMY weather files overcome the location misalignment issue by using real weather data from a recent historical year. Having a recent file also helps with some of the historical bias from constructing files from data up to 30 years old, but it does not capture future climate change-driven weather patterns. A potential problem with AMY is that it inherits any abnormalities that occurred in a given year. For example, if a particular year was unusually cold, cooling demands would be lower than you might generally see and heating loads a bit higher.  In ResStock, we generally run our models with both 2018 AMY and TMY weather~\citep{Bianchi2021}. 2018 is a year for which we have sufficient metered data for comparison, and it is also a compatible year for many grid simulation tools.

\subsubsection{Weather File Development}

Since ResStock is a composite model of many EnergyPlus models, it employs the standard EnergyPlus Weather (EPW) files (\cite{BigLadderSoftware2015}). The EPW weather format provides a timeseries dataset of a wide array of weather variables across all 8,760 hours of a non-leap year. These weather variables provide the climatic inputs for simulating heat transfer at each time step for each model within ResStock. For the TMY files, we use the most recent release, TMY3 from \citet{Wilcox2008}.\footnote{In review of the TMY3 data, we have identified some outliers in the initially published TMY3 data (e.g., erroneous temperature spikes). We have corrected those for ResStock use and published our corrected versions \citep{Bianchi2021}. }  For AMY,  we construct our own EPW files for internal use that are not available to the public. Some of the weather variables needed to construct an EPW are available on the \href{https://data.openei.org/submissions/4520}{Load Profiles OEDI submission}.

We develop custom AMY weather data files by pulling historic hourly temperature, humidity, wind speed/direction, and atmospheric pressure from the \href{https://www.ncei.noaa.gov/products/land-based-station/integrated-surface-database}{Integrated Surface Database}, developed by the National Oceanic and Atmospheric Administration's National Climatic Data Center. Additionally, we add in satellite-derived solar radiation data from NLR’s National Solar Radiation Database~\citep{nsrdb}. Ground-based solar radiation data are not widely collected, so using satellite-derived solar radiation data is standard practice for both the solar industry and building energy modelers using historical weather data. Caveats and further information on the data compilation and gap filling of this custom AMY approach can be found in Section 2.4 of \citet{Wilson2022}.

\subsubsection{Mapping Weather Files to ResStock Samples}
To produce weather files for ResStock, we develop AMY EPWs for approximately 1,200 weather stations pulling data from the year 2018---with the 2018 AMY roughly mapping to the locations of the TMY3 data.\footnote{Occasionally nearby stations are used if data are missing from the target weather station.} In ResStock, each county is assigned one of these available 1,200  weather stations. Each county will receive a weather station that is located in the county if one is available; if not, the county will be assigned a weather station closest to the county's population centroid, with prioritization of stations in the same climate zone. Timestamps are shifted if the chosen weather file is in a different time zone. All housing units within a given county will use the assigned weather data for that county for simulations. Within the model, actual weather file assignment occurs in the options\_lookup.tsv as a parameter input into the ResStockArguments script.

\subsubsection{Weather Files and Equipment Sizing}
In addition to the 8,760 timeseries of weather variables in the timeseries energy simulation, EPW files also provide a header with basic information on the weather location. ResStock uses some of this header information for sizing HVAC equipment---see Table \ref{Tab:Packages}.
%% FUTURE More detail on how we do sizing from headers

\begin{table}[!h]
 \centering
    \caption{Relevant fields from the EPW header}
    \label{Tab:Packages}
    \begin{tabular}{llp{0.6\textwidth}}
      \toprule
      Field          & Layer & Application                                                                           \\
      \midrule
      %accessibility & tagged & generates the document structure and tagging \\
      LOCATION &     OS-HPXML &                  OS-HPXML uses the stated latitude, longitude, and elevation in the EPW header. \\
      DESIGN CONDITIONS  & OS-HPXML                      & The design conditions of the EPW header are used in sizing HVAC equipment according to ACCA Manual J and system selection according to ACCA Manual S.\\
      GROUND TEMPERATURES  & N/A                      & Unused by ResStock. Instead OS-HPXML uses an analytical method to convert weather station temperatures to ground temperatures \citep{Xing2014}. \\
      HOLIDAYS/DAYLIGHT SAVINGS  & N/A                           & Unused by ResStock. Instead OS-HPXML models daylight savings in all states other than Arizona and Hawaii. \\
      \bottomrule
    \end{tabular}
  \end{table}
\section{Geometry}

In this section, we discuss the inputs that control the actual geometry of the building energy model used for simulation of each sample. We discuss the geometry parameters in five categories: housing unit location, building type, construction year, housing unit geometry, and space geometry.

\subsection{Housing Unit Location}

There are two reference frames for locating the housing units modeled in ResStock: (1) the building frame of reference and (2) the polar reference frame. The building frame defines the front, back, top, bottom, left, and right sides of the unit. The polar reference frame defines the orientation of the unit's front door with respect to the cardinal directions north, south, east, and west.

In ResStock, housing units are modeled as single zones, regardless if they are in larger buildings. To do this, adiabatic walls are assigned/modeled for walls, ceilings, or floors shared between the modeled housing unit, an adjacent unit, and a corridor.
%For identifying adiabatic walls, the process starts with distributions for the number of units in the building where the unit model is located. There are different distributions for the number of units in the building for single-family attached and multi-family units. The number of units characteristics are Geometry Building Number of Units MF and Geometry Building Number of Units SFA. Next, the number of stories is sampled in the Geometry Stories characteristic. Once a number of units for the building and the number of stories are sampled for the model, the horizontal and vertical locations of the unit are sampled in the Geometry Building Horizontal Location MF, Geometry Building Horizontal Location SFA, and Geometry Building Level MF characteristics.

%Single-family attached units have the possibility of their right and left sides being adiabatic. If the single-family attached unit is an end unit, one of the walls are adiabatic (the right or the left side). If the single-family attached unit is a middle unit both the left and right walls of the unit are adiabatic. Multi-family units follow the same rules as single-family attached, but add if the unit is a top, bottom, or middle unit. If the multi-family unit is a middle unit the top, bottom, left, and right walls are adiabatic. If the multi-family unit is a top unit, the bottom wall (floor) is adiabatic. If the multi-family unit is a bottom unit the top wall (ceiling) is adiabatic. For top and bottom multi-family units, left and right adiabatic walls are determined using the horizontal position {\footnote{see discussion of single-family attached units previously in this paragraph}. Single-family attached units the front and back are heat transfer surfaces. Multi-family units in ResStock have a front heat transfer surface, while the back is adiabatic (connected to an interior double corridor)}.

The units are shaded by how near other buildings are to the modeled unit.  OpenStudio-HPXML can model shading with exterior corridors for multifamily units, but ResStock does not use these capabilities for multifamily or single-family attached units.

The height above grade for the unit is based on the the number of floors the average ceiling height and the unit level (top floor, middle floors, or bottom floor). The height above grade largely impacts the importance of wind driven infiltration. For bottom units the above grade height is 0 ft. For middle units, the average height of all middle units is used. For top units, the height of the top floor.

There are 12 input files controlling building siting in ResStock:

\begin{itemize}
    \item Orientation
    \item Geometry Stories
    \item Geometry Stories Bin
    \item Geometry Building Type Height
    \item Geometry Stories Low Rise
    \item Geometry Building Number Units MF
    \item Geometry Building Number Units SFA
    \item Geometry Building Level MF
    \item Geometry Building Horizontal Location MF
    \item Geometry Building Horizontal Location SFA
    \item Neighbors
    \item Corridor.

\end{itemize}

\subsubsection{Orientation} \label{sec:orientation}
\input{characteristics/Orientation}

\subsubsection{Geometry Stories}
\input{characteristics/Geometry Stories}

\subsubsection{Geometry Story Bin}
\input{characteristics/Geometry Story Bin}

\subsubsection{Geometry Building Type Height}
\input{characteristics/Geometry Building Type Height}

\subsubsection{Geometry Stories Low Rise}
\input{characteristics/Geometry Stories Low Rise}

\subsubsection{Geometry Building Number Units MF}
\input{characteristics/Geometry Building Number Units MF}

\subsubsection{Geometry Building Number Units SFA}
\input{characteristics/Geometry Building Number Units SFA}

\subsubsection{Geometry Building Level MF}
\input{characteristics/Geometry Building Level MF}

\subsubsection{Geometry Building Horizontal Location MF}
\input{characteristics/Geometry Building Horizontal Location MF}

\subsubsection{Geometry Building Horizontal Location SFA}
\input{characteristics/Geometry Building Horizontal Location SFA}

\subsubsection{Neighbors}
\input{characteristics/Neighbors}

\subsubsection{Corridor}
\input{characteristics/Corridor}

\subsection{Building Type}
This section discusses the ResStock input files that control tagging and model differentiation of building type.  These building types control a lot of assumptions and treatment of variables in the OpenStudio-HPXML workflow. An example is that the plug load energy is based on a regression equation, and the equation coefficients are different between the building types.

There are two input files controlling building type assignment in ResStock:

\begin{itemize}
    \item Geometry Building Type ACS
    \item Geometry Building Type RECS.
\end{itemize}

\subsubsection{Geometry Building Type ACS}
\input{characteristics/Geometry Building Type ACS}

\subsubsection{Geometry Building Type RECS}
\input{characteristics/Geometry Building Type RECS}

\subsection{Construction Year}
ResStock captures the change in energy codes over time by relying on survey data (mainly from ACS and EIA RECS) to inform how housing units have adopted energy code vintages and retrofits over time. The approach used in ResStock is to assign a decadal bin when the building was constructed. The decadal bins range from pre-1940s to the 2010s. The Vintage and Vintage ACS characteristics are then used as dependencies to assign probabilities for each Vintage bin. For example, wall insulation being dependent on vintage allows the wall insulation R-value mean to increase over time.

There are two input files controlling building type assignment in ResStock:

\begin{itemize}
    \item Vintage
    \item Vintage ACS.
\end{itemize}

\subsubsection{Vintage}
\input{characteristics/Vintage}

\subsubsection{Vintage ACS}
\input{characteristics/Vintage ACS}

\subsection{Housing Unit Geometry}

There are seven input files controlling housing unit geometry in ResStock:

\begin{itemize}
    \item Geometry Building Floor Area
    \item Geometry Building Floor Area Bin
    \item Bedrooms
    \item Geometry Attic Type
    \item Geometry Foundation Type
    \item Geometry Garage
    \item Geometry Space Combination.
\end{itemize}

\subsubsection{Geometry Floor Area}
\input{characteristics/Geometry Floor Area}

\subsubsection{Geometry Floor Area Bin}
\input{characteristics/Geometry Floor Area Bin}

\subsection{Space Geometry}
\label{space_geometry}

\subsubsection{Bedrooms}
\input{characteristics/Bedrooms}

\subsubsection{Geometry Attic Type}
\input{characteristics/Geometry Attic Type}

\subsubsection{Geometry Foundation Type} \label{geometry_foundation_type}
\input{characteristics/Geometry Foundation Type}

\subsubsection{Geometry Garage}
\input{characteristics/Geometry Garage}

\subsubsection{Geometry Space Combination}
\input{characteristics/Geometry Space Combination}

\section{Envelope}

The envelope components of ResStock inputs interface closely with the Geometry inputs, but focus more on the materials and thermal properties of the envelope. In this section, we discuss the various input files that control the modeled envelope in ResStock by envelope component.

\subsection{Walls}

There are three major input files to ResStock that control the wall properties:
\begin{itemize}
    \item Geometry Wall Type
    \item Geometry Wall Exterior Finish
    \item Insulation Wall.
\end{itemize}

Collectively, they specify the material choices and R-value of the housing unit walls.

\subsubsection{Geometry Wall Type}\label{geometry_wall_type}
\input{characteristics/Geometry Wall Type}

\subsubsection{Geometry Wall Exterior Finish}\label{geometry_wall_exterior_finish}
\input{characteristics/Geometry Wall Exterior Finish}

\subsubsection{Insulation Wall}\label{insulation_wall}
\input{characteristics/Insulation Wall}

\subsection{Roof and Ceiling}

There are three input files describing thermal properties of the roof and/or ceilings of housing units:
\begin{itemize}
    \item Insulation Roof
    \item Insulation Ceiling
    \item Roof Material.
\end{itemize}

Additionally, there is an input for defining Radiant Barriers in homes with attics, but it is not currently used in ResStock.

A major assumption in ResStock is that multifamily buildings and mobile homes do not have attics (see Section \ref{space_geometry}), so their insulation is assigned in Insulation Ceiling, while for other building types it is assigned in the Insulation Roof housing characteristic.

\subsubsection{Insulation Roof}\label{insulation_roof}
\input{characteristics/Insulation Roof}

\subsubsection{Radiant Barrier}\label{radiant_barrier}
\input{characteristics/Radiant Barrier}

\subsubsection{Roof Material}\label{roof_material}
\input{characteristics/Roof Material}

\subsubsection{Insulation Ceiling}\label{insulation_ceiling}
\input{characteristics/Insulation Ceiling}

\subsection{Foundation}
Five input files specify insulation and heat transfer parameters with the ground:
\begin{itemize}
    \item Insulation Floor
    \item Insulation Foundation Wall
    \item Insulation Rim Joist
    \item Insulation Slab
    \item Ground Thermal Conductivity.
\end{itemize}

The inputs starting with ``Insulation'' specify insulation levels that vary depending upon Geometry Foundation Type (Section \ref{geometry_foundation_type}).
%%%%%%%%%%%%%%%
\subsubsection{Insulation Floor}\label{insulation_floor}
\input{characteristics/Insulation Floor}

\subsubsection{Insulation Slab}\label{insulation_slab}
\input{characteristics/Insulation Slab}

\subsubsection{Insulation Foundation Wall}\label{insulation_foundation_wall}
\input{characteristics/Insulation Foundation Wall}

\subsubsection{Insulation Rim Joist}\label{insulation_rim_joist}
\input{characteristics/Insulation Rim Joist}

\subsubsection{Ground Thermal Conductivity}\label{ground_thermal_conductivity}
\input{characteristics/Ground Thermal Conductivity}

\subsection{Doors and Windows}
In ResStock, two input files control door specification in ResStock:
\begin{itemize}
    \item Doors
    \item Door Area.
\end{itemize}

Two similar input files specify windows:
\begin{itemize}
    \item Windows
    \item Window Areas.
\end{itemize}

Discussed also in this section are building features that might impact shading in windows. All three of these inputs are either not used or have constant values for the entire stock:
\begin{itemize}
    \item Interior Shading
    \item Eaves.
\end{itemize}

\subsubsection{Door Area}\label{door_area}
\input{characteristics/Door Area}

\subsubsection{Doors}\label{doors}
\input{characteristics/Doors}

\subsubsection{Windows}\label{windows}
\input{characteristics/Windows}

\subsubsection{Window Areas}\label{window_areas}
\input{characteristics/Window Areas}

\subsubsection{Eaves}\label{eaves}
\input{characteristics/Eaves}

\subsubsection{Interior Shading}\label{interior_shading}
\input{characteristics/Interior Shading}

\subsection{Infiltration}
Infiltration is air leakage between the envelope and the outdoor environment. In the U.S.~residential sector, it is the leading driver of heating and cooling loads (compared to, for example, heat transfer through other parts of the envelope). In ResStock, infiltration is controlled by a single input file that provides a whole-home infiltration rate.

\subsubsection{Infiltration}\label{infiltration}
\input{characteristics/Infiltration}
