\documentclass[]{nrel}

\usepackage{lipsum} 
\usepackage{longtable}
\usepackage{ragged2e}
\usepackage{comment}
\usepackage{caption}
\usepackage{hyperref}

\newenvironment{customLongTable}[4]{ % #1 is format, #2 is caption, #3 is label, #4 is header row
    \begin{longtable}{#1}
        \captionsetup{list=yes}
        \caption{#2} \label{#3} \\
        \toprule
        #4 \\
        \endfirsthead

        \captionsetup{list=no}
        \caption[]{#2 (continued)} \\ % Continuation caption
        \toprule
        #4 \\
        \endhead

        \bottomrule
}{
        \bottomrule
    \end{longtable}
}

\hypersetup{colorlinks=true, urlcolor=nrelblue}
% -----------------------------------
% DOCUMENT PROPERTIES
% -----------------------------------
\title{ResStock Technical Reference Documentation, Active Development Version}

\author{Janet Reyna} 
\author{Anthony Fontanini}
\author{Elaina Present} 
\author{Lixi Liu} 

\author{Rajendra Adhikari}
\author{Carlo Bianchi}
\author{Jes Brossman}
\author{Rohit Chintala}
\author{Kenya Clark}
\author{Chioke Harris}
\author{Scott Horowitz}
\author{Yingli Lou}
\author{Jeff Maguire}
\author{Noel Merket}
\author{Nathan Moore}
\author{Prateek Munankarmi}
\author{Joseph Robertson}
\author{Noah Sandoval}
\author{Andrew Speake}
\author{Katelyn Stenger}
\author{Philip White}
\author{Eric Wilson}

\affil{National Renewable Energy Laboratory}


\fancypagestyle{plain}{}
\addbibresource{files/refs.bib}
\setcounter{tocdepth}{2}

% -------------------------------------
% DOCUMENT STARTS HERE
% -------------------------------------
\begin{document}

\frontmatter
\chapter{Executive Summary}

\section*{What Is ResStock?}

ResStock\textsuperscript{TM} is the best-in-class building stock energy model for simulating and publishing energy use, utility bills, and greenhouse gas emissions from the residential sector of the United States. ResStock answers two primary questions: (1) How and when is energy used in the U.S.~residential building stock? and (2) What are the impacts of technological and behavioral changes in U.S.~homes? Specifically, ResStock quantifies energy use at high granularity, while maintaining heterogeneity, across geographical locations, demographic groups, home types, fuels, end uses, and time of day. Additionally, it details the impact of efficiency, technology fuel changes, or energy flexibility measures: total changes in the amount of energy used by measure; where or in what use cases upgrade measures save energy; when or at what times of day savings occur; and which building stock or demographic segments have the biggest savings potential. This model, and the public datasets it produces, are foundational to identifying pathways to affordable and resilient energy use in the U.S.~residential buildings sector.

\section*{Motivation}

The primary objective of ResStock is to empower decision makers to make data-driven choices to improve energy affordability, comfort, and resilience in the U.S. housing sector.  Across the United States, increasing numbers of cities, counties, and states are setting goals around energy use and associated metrics. Although much of this planning rightfully focuses on the electric grid, the on-site combustion of fossil fuels in U.S.~homes, primarily for space and water heating, accounts for 56\% of on-site energy usage. Furthermore, pathways to improving the resiliency and reliability of the electric grid are highly dependent upon the future timing and magnitude of electricity demand. Buildings currently comprise 74\% of electricity demand in the United States~\citep{MER2023}, and this could grow with electric vehicle adoption. Much of the work in supporting grid resiliency through building sector demand will fall on state and local government staff, the engineering and policy consulting communities, and advocacy and research organizations to ensure that these goals are realistic, achievable, and distributed appropriately. ResStock was developed by the National Renewable Energy Laboratory (NREL) with funding from the U.S.~Department of Energy (DOE) to assist the professionals and researchers tasked with implementing these initiatives.

\section*{How Is ResStock Accessed?}

The ResStock model and its published datasets are foundational for a wide range of stakeholders. Professionals and researchers have several pathways for using ResStock data and insights. They can review published fact sheets and reports based upon ResStock data. They can use a web-based visualization platform to interact with the dataset of annual and timeseries results, or they can use a simple spreadsheet-type analysis to interact with annual energy consumption results and aggregated timeseries load profiles. If users want to go deeper, they can even use the raw simulation results dataset, which may require big-data skills and cloud or high-performance computing assets. 

\section*{Impact}

The ResStock data viewer for the public data has to date been accessed by accounts from 5,724 unique email addresses across 1,907 domain names that mainly support consultants, utilities, city, county, and local governments, state offices, DOE, and other federal offices. It is estimated that the datasets that ResStock produces are used by utilities that serve over 38\% of the U.S.~population (126 million people), 5 regional energy efficiency offices, 12 state energy offices, and 3 public utility commissions. In fiscal year 2024, the combined ResStock and ComStock datasets had 18.4 million unique data file downloads from the Open Energy Dataset Initiative (OEDI), including datasets derived from End-Use Load Profiles (EULP) (82\% of all OEDI downloads), as of July 31, 2024.

%% Add citation statistics

\section*{Purpose of This Document}

The purpose of this document is to provide a central technical reference of the ResStock baseline. ResStock is a complex model with code spread across multiple repositories. The goal is to provide the central theory and arguments in a single location with clear references to underlying models and software for users who need additional detail.

\chapter{Acknowledgments}
Since initial development over a decade ago, ResStock has had dozens of researchers contribute to the structure, features, theory, and publication of data. In particular, we'd like to acknowledge Craig Christensen, who was instrumental in the initial model development. Additionally, we'd like to acknowledge our peer reviewers on this document: Andrew Parker and Jon Winkler. Additionally, we'd like to acknowledge U.S. Department of Energy (DOE) staff who have supported and guided ResStock development, including Dale Hoffmeyer, Amir Roth, Gretchen Maia, Asa Foss, Amy Royden-Bloom, and Eric Werling of the Building Technologies Office; Joan Glickman of the Office of State and Community Energy Programs; John Agan, Jenah Zweig, and Erin Boyd of the Office of Policy; and Robert Weber of the Bonneville Power Administration. Additionally, ResStock has been improved upon through work for parties outside of DOE, most notably the Los Angeles Department of Water and Power. We also would like to acknowledge the work of the EnergyPlus\textsuperscript{\textregistered} whole-building energy modeling tool, the OpenStudio\textsuperscript{\textregistered} SDK, and the OpenStudio-HPXML schema implementation, which provide the foundational model underpinnings of energy simulation in ResStock and which are the result of years of hard work by many people across DOE, the national laboratories, and the private sector.

This work was authored by the National Renewable Energy Laboratory, operated by Alliance for Sustainable Energy, LLC, for the U.S. Department of Energy (DOE) under Contract No. DE-AC36-08GO28308. Funding provided by U.S. Department of Energy Office of Energy Efficiency and Renewable Energy Building Technologies Office. The views expressed in the article do not necessarily represent the views of the DOE or the U.S. Government. 

A portion of this research was performed using computational resources sponsored by the U.S. Department of Energy's Office of Energy Efficiency and Renewable Energy and located at the National Renewable Energy Laboratory.

%%%%%%%%
\chapter{Version History}

\vspace{1cm}

\begin{center}
\begin{tabular}{ |c || c c c c|}
\hline
 Technical Reference Documentation & Standard Data Release & ResStock & BuildStock Batch  & OpenStudio-HPXML \\ \hline \hline
 v1.0.0, January 2025 & \href{https://resstock.nrel.gov/datasets}{2024.2} & \href{https://github.com/NREL/resstock/tree/v3.3.0}{v3.3.0} &  \href{https://buildstockbatch.readthedocs.io/en/v2023.10.0/index.html} {v2023.10.0} & \href{https://github.com/NREL/OpenStudio-HPXML/tree/v1.8.1}{v1.8.0} \\\hline
 
\end{tabular}
\end{center}


%%%%%%%%%%%%%%%%%%%%%%%%%%% 
\chapter{List of Acronyms}

\begin{acronym}
\acro {ACCA} {Air Conditioning Contractors of America}
\acro {ACH} {air changes per hour}
\acro {ACS} {American Community Survey}
\acro {AFUE} {Annual Fuel Utilization Efficiency}
\acro {AIANNH}{American Indian/Alaska Native/Native Hawaiian}
\acro {AMY}{Actual Meteorological Year}
\acro {ASHP}{air-source heat pump}
\acro {ATUS}{American Time Use Survey}
\acro {AWS}{Amazon Web Services}
\acro {CBSA}{Core-Based Statistical Area}
\acro {CEC}{California Energy Commission}
\acro {CEER}{combined energy efficiency ratio}
\acro {CFL}{compact florescent bulb}
\acro {CFM}{cubic feet per minute}
\acro {COP}{coefficient of performance}
\acro {CRAK}{Custom Region Alaska}
\acro {CRHI}{Custom Region Hawaii}
\acro {DOE}{U.S.~Department of Energy}
\acro {EER}{energy efficiency ratio}
\acro {EF}	{Energy Factor}
\acro {EIA}{U.S.~Energy Information Administration}
\acro {EPW}{EnergyPlus Weather file}
\acro {EV}{Electric vehicle}
\acro {FPL}{federal poverty level}
\acro {GEA}{Generation and Emissions Assessment}
\acro {HERS}{Home Energy Rating System}
\acro {HIFLD}{Homeland Infrastructure Foundation-Level Data}
\acro {HPC}{high-performance computing}
\acro {HSPF}	Heating Seasonal Performance Factor
\acro {HVAC}{heating, ventilating, and air conditioning}
\acro {LBNL}{Lawrence Berkeley National Laboratory}
\acro {LED}{light-emitting diode}
\acro {LIHEAP}{Low-Income Home Energy Assistance Program}
\acro {MELS} {Miscellaneous Electric Loads}
\acro {MF}{multifamily}
\acro {MSA}{Metropolitan Statistical Area}
\acro {MSHP}{mini-split heat pump}
\acro {NEEA}{Northwest Energy Efficiency Alliance}
\acro {NFRC}{National Fenestration Rating Council}
\acro {NHTS}{National Household Travel Survey}
\acro {NREL}{National Renewable Energy Laboratory}
\acro {OEDI}{Open Energy Dataset Initiative}
\acro {PUMA}{Public Use Microdata Area}
\acro {PUMS}{Public Use Microdata Samples}
\acro {PV}{photovoltaic}
\acro {RBSA}{Residential Building Stock Assessment}
\acro {RECS} {Residential Energy Consumption Survey}
\acro {ResDB}{Residential Diagnostics Database}
\acro {SEER}{Seasonal Energy Efficiency Ratio}
\acro {SFA}{single-family attached}
\acro {SFD}{single-family detached}
\acro {TEMPO}{Transportation Energy \& Mobility Pathway Options Model}
\acro {TMY}{Typical Meteorological Year}
\acro {WWR}{window-to-wall ratio}

\end{acronym}

\mainmatter
\tableofcontents
\listoffigures
\listoftables

\input{1_Introduction.tex}
\input{2_ResStockStructureAndSampling.tex}
\input{3a_ResStockInputs.tex}
\input{3b_ResStockInputs_HVAC.tex}
\input{3c_ResStockInputs.tex}
% \input{4_RunningResStock.tex}
\input{5_ResStockOutputs.tex}
\input{6_PublicDataAccess.tex}
% PRIORITY C \input{7_Validation.tex}
% PRIORITY B \input{8_KnownIssues.tex}
% PRIORITY C \input{9_Changelog.tex}

% bibliography
\cleardoublepage
\label{sec:Bib}
\printbibliography[title={\LARGE References}]
\addcontentsline{toc}{chapter}{References}
% \nocite{*}

%\begin{appendices} %<--------- All chapters after this will be labeled as appendices
%  \appchapter{ResStock Input Detailed Documentation}
%  \input{Appendix_ResStock-RTD}
%\end{appendices}
\end{document}
