\begin{customLongTable}{ |p{5cm}|p{3cm}|p{7cm}| }
{The ResStock properties set in the Hot Water Distribution characteristic} {table:hc_arg_def_hot_water_distribution}
{Name & Units & Description}
\texttt{dhw\_distribution\_pipe\_insulation\_nominal\_r\_value} & F-ft2-hr/Btu & Nominal R-value of the pipe insulation.  \\ \hline
\texttt{dhw\_distribution\_system\_type} &  & The type of hot water distribution system.  \\ \hline
\texttt{dhw\_distribution\_standard\_piping\_length} & ft & If the system type is Standard, the length of hot water piping from the hot water heater to the farthest hot water fixture, measured longitudinally from plans, assuming the hot water piping does not run diagonally, plus 10 feet of piping for each floor level, plus 5 feet of piping for unconditioned basements (if any).  \\ \hline
\texttt{dhw\_distribution\_recirculation\_control\_type} &  & If the system type is Recirculation, the type of hot water recirculation control, if any.  \\ \hline
\texttt{dhw\_distribution\_recirculation\_piping\_loop\_length} & ft & If the system type is Recirculation, the recirculation loop length including both supply and return sides, measured longitudinally from plans, assuming the hot water piping does not run diagonally, plus 20 feet of piping for each floor level greater than one plus 10 feet of piping for unconditioned basements.  \\ \hline
\texttt{dhw\_distribution\_recirculation\_branch\_piping\_length} & ft & If the system type is Recirculation, the length of the branch hot water piping from the recirculation loop to the farthest hot water fixture from the recirculation loop, measured longitudinally from plans, assuming the branch hot water piping does not run diagonally.  \\ \hline
\texttt{dhw\_distribution\_recirculation\_pump\_power} & W & If the system type is Recirculation, the recirculation pump power.  \\
\texttt{dhw\_fixtures\_low\_flow\_showers} &  & Whether the shower fixtures are low flow (<= 2.0 gpm).  \\ \hline
\texttt{dhw\_fixtures\_low\_flow\_sinks} &  & Whether the sink fixtures are low flow (<= 2.0 gpm).  \\ \hline
\texttt{dhw\_fixtures\_usage\_multiplier} &  & Multiplier on the hot water usage that can reflect, e.g., high/low usage occupants.  \\
\texttt{dhw\_drain\_water\_heat\_recovery\_efficiency} & frac & The efficiency of the DWHR according to CSA 55.1.  \\ \hline
\texttt{dhw\_drain\_water\_heat\_recovery\_facilities\_connected} &  & Use 'one' if there are All Showers and only one of them is connected to the DWHR. Use 'all' if there is one shower and it's connected to the DWHR or there are two or more showers connected to the DWHR.  \\ \hline
\texttt{dhw\_drain\_water\_heat\_recovery\_equal\_flow} &  & True if the DWHR supplies pre-heated water to both the fixture cold water piping and the hot water heater potable supply piping. False if the DWHR only supply pre-heated water to the hot water heater potable supply piping.  \\
\end{customLongTable}
