\begin{customLongTable}{ |p{5cm}|p{3cm}|p{7cm}| }
{The ResStock properties set in the HVAC Cooling Efficiency characteristic} {table:hc_arg_def_hvac_cooling_efficiency}
{Name & Units & Description}
\texttt{hvac\_cooling\_system\_type} &  & The type of system.  \\ \hline
\texttt{hvac\_cooling\_system\_cooling\_efficiency\_type} &  & The cooling efficiency type. Central ACs and Mini-Split ACs use SEER2 or EER2; Room ACs and Packaged Terminal ACs use CEER or EER.  \\ \hline
\texttt{hvac\_cooling\_system\_cooling\_efficiency} &  & The rated cooling efficiency.  \\ \hline
\texttt{hvac\_cooling\_system\_cooling\_compressor\_type} &  & The compressor type of the cooling system. Applies to Central ACs and Mini-Split ACs.  \\ \hline
\texttt{hvac\_cooling\_system\_detailed\_performance\_data\_capacity\_type} &  & Type of capacity values when providing detailed performance data. Applies to Central ACs and Mini-Split ACs.  \\ \hline
\texttt{hvac\_cooling\_system\_detailed\_performance\_data\_cooling\_outdoor\_temperatures} & F & List of outdoor temperatures when providing detailed performance data. Applies to Central ACs and Mini-Split ACs.  \\ \hline
\texttt{hvac\_cooling\_system\_detailed\_performance\_data\_cooling\_min\_speed\_capacities} & Btu/hr or Frac & Minimum speed capacities when providing detailed performance data.  Applies to Central ACs and Mini-Split ACs.  \\ \hline
\texttt{hvac\_cooling\_system\_detailed\_performance\_data\_cooling\_nom\_speed\_capacities} & Btu/hr or Frac & Nominal speed capacities when providing detailed performance data.  Applies to Central ACs and Mini-Split ACs.  \\ \hline
\texttt{hvac\_cooling\_system\_detailed\_performance\_data\_cooling\_max\_speed\_capacities} & Btu/hr or Frac & Maximum speed capacities when providing detailed performance data.  Applies to Central ACs and Mini-Split ACs.  \\ \hline
\texttt{hvac\_cooling\_system\_detailed\_performance\_data\_cooling\_min\_speed\_cops} & W/W & Minimum speed COPs when providing detailed performance data.  Applies to Central ACs and Mini-Split ACs.  \\ \hline
\texttt{hvac\_cooling\_system\_detailed\_performance\_data\_cooling\_nom\_speed\_cops} & W/W & Nominal speed COPs when providing detailed performance data.  Applies to Central ACs and Mini-Split ACs.  \\ \hline
\texttt{hvac\_cooling\_system\_detailed\_performance\_data\_cooling\_max\_speed\_cops} & W/W & Maximum speed COPs when providing detailed performance data.  Applies to Central ACs and Mini-Split ACs.  \\
\texttt{hvac\_cooling\_system\_capacity\_capacity} & Btu/hr & The output capacity.  \\ \hline
\texttt{hvac\_cooling\_system\_capacity\_autosizing\_factor} & mult & A capacity scaling factor that can be applied to the autosizing methodology.  \\ \hline
\texttt{hvac\_cooling\_system\_capacity\_autosizing\_limit} & Btu/hr & A maximum capacity limit that can be applied to the autosizing methodology.  \\
\end{customLongTable}
