\begin{customLongTable}{ |p{5cm}|p{3cm}|p{7cm}| }
{The ResStock properties set in the HVAC Shared Efficiencies characteristic} {table:hc_arg_def_hvac_shared_efficiencies}
{Name & Units & Description}
\texttt{hvac\_heating\_system\_type} &  & The type of system. \\ \hline
\texttt{hvac\_heating\_system\_heating\_efficiency} & Frac & The rated heating efficiency. \\ \hline
\texttt{hvac\_heating\_system\_heating\_load\_served\_fraction} &  & Fraction of load served by the HVAC system. \\ \hline
\texttt{hvac\_cooling\_system\_type} &  & The type of system. \\ \hline
\texttt{hvac\_cooling\_system\_cooling\_efficiency\_type} &  & The cooling efficiency type. Central ACs and Mini-Split ACs use SEER2 or EER2; Room ACs and Packaged Terminal ACs use CEER or EER. \\ \hline
\texttt{hvac\_cooling\_system\_cooling\_efficiency} &  & The rated cooling efficiency. \\ \hline
\texttt{hvac\_cooling\_system\_cooling\_compressor\_type} &  & The compressor type of the cooling system. Applies to Central ACs and Mini-Split ACs. \\ \hline
\texttt{hvac\_heat\_pump\_type} &  & The type of system. \\ \hline
\texttt{hvac\_heat\_pump\_capacity\_autosizing\_methodology} &  & Logic for autosized heat pumps. \\ \hline
\texttt{hvac\_heat\_pump\_heating\_load\_served\_fraction} &  & Fraction of load served by the HVAC system. \\ \hline
\texttt{hvac\_heat\_pump\_cooling\_load\_served\_fraction} &  & Fraction of load served by the HVAC system. \\ \hline
\texttt{hvac\_heat\_pump\_backup\_type} &  & The backup type. Use 'integrated' to represent e.g. built-in electric strip heat or dual-fuel integrated furnace. Use 'separate' to represent e.g. electric baseboard or boiler (based on Heating System 2). \\ \hline
\texttt{hvac\_heating\_shared\_system} &  & The type of shared system. \\
\end{customLongTable}
