\begin{customLongTable}{ |p{5cm}|p{3cm}|p{7cm}| }
{The ResStock properties set in the Lighting characteristic} {table:hc_arg_def_lighting}
{Name & Units & Description}
\texttt{lighting\_interior\_fraction\_cfl} & frac & Fraction of all interior lamps that are compact fluorescent. Lighting not specified as CFL, LFL, or LED is assumed to be incandescent.  \\ \hline
\texttt{lighting\_interior\_fraction\_lfl} & frac & Fraction of all interior lamps that are linear fluorescent. Lighting not specified as CFL, LFL, or LED is assumed to be incandescent.  \\ \hline
\texttt{lighting\_interior\_fraction\_led} & frac & Fraction of all interior lamps that are light emitting diodes. Lighting not specified as CFL, LFL, or LED is assumed to be incandescent.  \\ \hline
\texttt{lighting\_interior\_usage\_multiplier} &  & Multiplier on the interior lighting energy usage that can reflect, e.g., high/low usage occupants.  \\ \hline
\texttt{lighting\_exterior\_fraction\_cfl} & frac & Fraction of all exterior lamps that are compact fluorescent. Lighting not specified as CFL, LFL, or LED is assumed to be incandescent.  \\ \hline
\texttt{lighting\_exterior\_fraction\_lfl} & frac & Fraction of all exterior lamps that are linear fluorescent. Lighting not specified as CFL, LFL, or LED is assumed to be incandescent.  \\ \hline
\texttt{lighting\_exterior\_fraction\_led} & frac & Fraction of all exterior lamps that are light emitting diodes. Lighting not specified as CFL, LFL, or LED is assumed to be incandescent.  \\ \hline
\texttt{lighting\_exterior\_usage\_multiplier} &  & Multiplier on the exterior lighting energy usage that can reflect, e.g., high/low usage occupants.  \\ \hline
\texttt{lighting\_garage\_fraction\_cfl} & frac & Fraction of all garage lamps that are compact fluorescent. Lighting not specified as CFL, LFL, or LED is assumed to be incandescent.  \\ \hline
\texttt{lighting\_garage\_fraction\_lfl} & frac & Fraction of all garage lamps that are linear fluorescent. Lighting not specified as CFL, LFL, or LED is assumed to be incandescent.  \\ \hline
\texttt{lighting\_garage\_fraction\_led} & frac & Fraction of all garage lamps that are light emitting diodes. Lighting not specified as CFL, LFL, or LED is assumed to be incandescent.  \\ \hline
\texttt{lighting\_garage\_usage\_multiplier} &  & Multiplier on the garage lighting energy usage that can reflect, e.g., high/low usage occupants.  \\
\end{customLongTable}
