\begin{customLongTable}{ |p{5cm}|p{3cm}|p{7cm}| }
{The ResStock properties set in the Mechanical Ventilation characteristic} {table:hc_arg_def_mechanical_ventilation}
{Name & Units & Description}
\texttt{ventilation\_mechanical\_fan\_type} &  & The type of the mechanical ventilation.  \\ \hline
\texttt{ventilation\_mechanical\_sensible\_recovery\_efficiency} & frac & The sensible recovery efficiency for heating mode. Applies to HRVs and ERVs only.  \\ \hline
\texttt{ventilation\_mechanical\_total\_recovery\_efficiency} & frac & The total recovery efficiency. Applies to ERVs only.  \\ \hline
\texttt{ventilation\_mechanical\_flow\_rate} & cfm & The flow rate of the mechanical ventilation.  \\ \hline
\texttt{ventilation\_mechanical\_fan\_power} & W & The fan power of the mechanical ventilation.  \\ \hline
\texttt{ventilation\_mechanical\_hours\_in\_operation} & hrs/day & The hours in operation of the mechanical ventilation.  \\
\texttt{ventilation\_kitchen\_flow\_rate} & cfm & The flow rate for each kitchen fan.  \\ \hline
\texttt{ventilation\_kitchen\_hours\_in\_operation} & hrs/day & The hours per day of operation for each kitchen fan.  \\ \hline
\texttt{ventilation\_kitchen\_fan\_power} & W & The fan power for each kitchen fan.  \\ \hline
\texttt{ventilation\_kitchen\_start\_hour} & hr & The start hour for each kitchen fan.  \\ \hline
\texttt{ventilation\_kitchen\_count} &  & The number of kitchen fans in the home.  \\
\texttt{ventilation\_bathroom\_flow\_rate} & cfm & The flow rate for each bathroom fan.  \\ \hline
\texttt{ventilation\_bathroom\_hours\_in\_operation} & hrs/day & The hours per day of operation for each bathroom fan.  \\ \hline
\texttt{ventilation\_bathroom\_fan\_power} & W & The fan power for each bathroom fan.  \\ \hline
\texttt{ventilation\_bathroom\_start\_hour} & hr & The start hour for each bathroom fan.  \\ \hline
\texttt{ventilation\_bathroom\_count} &  & The number of bathroom fans in the home.  \\
\texttt{ventilation\_whole\_house\_fan\_rated\_flow\_rate} & cfm & The rated flow rate of the whole house fan.  \\ \hline
\texttt{ventilation\_whole\_house\_fan\_power} & W & The fan power of the whole house fan.  \\
\end{customLongTable}
