\begin{customLongTable}{ |p{5cm}|p{3cm}|p{7cm}| }
{The ResStock properties set in the Water Heater Efficiency characteristic} {table:hc_arg_def_water_heater_efficiency}
{Name & Units & Description}
\texttt{dhw\_water\_heater\_type} &  & The type of water heater.  \\ \hline
\texttt{dhw\_water\_heater\_fuel\_type} &  & The fuel type of the water heater.  \\ \hline
\texttt{dhw\_water\_heater\_efficiency\_type} &  & The efficiency type of the water heater. Does not apply to space-heating boilers.  \\ \hline
\texttt{dhw\_water\_heater\_efficiency} &  & EnergyGuide Label rated Uniform Energy Factor (UEF) or Energy Factor (EF).  \\ \hline
\texttt{dhw\_water\_heater\_tank\_volume} & gal & The nominal volume of the water heater storage tank.  \\ \hline
\texttt{dhw\_water\_heater\_recovery\_efficiency} & frac & Ratio of energy delivered to water heater to the energy content of the fuel consumed by the water heater. Only used for non-electric storage water heaters.  \\ \hline
\texttt{dhw\_water\_heater\_usage\_bin} &  & EnergyGuide label usage bin (based on First Hour Rating).  \\ \hline
\texttt{dhw\_water\_heater\_temperature} & F & The setpoint temperature of water heater.  \\
\texttt{dhw\_solar\_thermal\_collector\_loop\_type} &  & The loop type of the solar thermal system.  \\ \hline
\texttt{dhw\_solar\_thermal\_collector\_type} &  & The type of collector.  \\ \hline
\texttt{dhw\_solar\_thermal\_collector\_area} &  & The surface area for the collector.  \\ \hline
\texttt{dhw\_solar\_thermal\_collector\_rated\_optical\_efficiency} &  & FRTA (y-intercept) from the Directory of SRCC OG-100 Certified Solar Collector Ratings.  \\ \hline
\texttt{dhw\_solar\_thermal\_collector\_rated\_thermal\_losses} &  & FRUL (slope) from the Directory of SRCC OG-100 Certified Solar Collector Ratings  \\ \hline
\texttt{dhw\_solar\_thermal\_storage\_volume} &  & Hot water storage volume.  \\ \hline
\texttt{dhw\_solar\_thermal\_solar\_fraction} &  & Portion of total conventional hot water heating load (delivered energy plus tank standby losses). Can be obtained from Directory of SRCC OG-300 Solar Water Heating System Ratings or NREL's System Advisor Model or equivalent.  \\
\texttt{dhw\_solar\_thermal\_direction\_collector\_azimuth} & deg & The azimuth of the solar thermal system collectors. Azimuth is measured clockwise from north (e.g., North=0, East=90, South=180, West=270).  \\ \hline
\texttt{dhw\_solar\_thermal\_direction\_collector\_tilt} & deg & The tilt of the solar thermal system collectors. Defaults to roof pitch.  \\
\texttt{dhw\_water\_heater\_jacket\_rvalue} & h-ft\textsuperscript{2}-R/Btu & The jacket R-value of the storage water heater.  \\
\end{customLongTable}
