\begin{customLongTable}{ |p{2.5cm}|p{1.5cm}|p{2.5cm}|p{1.1cm}|p{2.9cm}|p{3cm}| }
{The ResStock argument definitions set in the Neighbors characteristic} {table:hc_arg_def_neighbors}
{Name & Required & Units & Type & Choices & Description}
\texttt{neighbor\_front\_distance} & true & ft & Double &  & The distance between the unit and the neighboring building to the front (not including eaves). A value of zero indicates no neighbors. Used for shading.  \\ \hline
\texttt{neighbor\_back\_distance} & true & ft & Double &  & The distance between the unit and the neighboring building to the back (not including eaves). A value of zero indicates no neighbors. Used for shading.  \\ \hline
\texttt{neighbor\_left\_distance} & true & ft & Double &  & The distance between the unit and the neighboring building to the left (not including eaves). A value of zero indicates no neighbors. Used for shading.  \\ \hline
\texttt{neighbor\_right\_distance} & true & ft & Double &  & The distance between the unit and the neighboring building to the right (not including eaves). A value of zero indicates no neighbors. Used for shading.  \\ \hline
\texttt{neighbor\_front\_height} & false & ft & Double & auto & The height of the neighboring building to the front.   \\ \hline
\texttt{neighbor\_back\_height} & false & ft & Double & auto & The height of the neighboring building to the back.   \\ \hline
\texttt{neighbor\_left\_height} & false & ft & Double & auto & The height of the neighboring building to the left.   \\ \hline
\texttt{neighbor\_right\_height} & false & ft & Double & auto & The height of the neighboring building to the right.   \\
\end{customLongTable}
